---
title: "Untitled"
author: "Mathis Gheno"
date: "2024-12-05"
output: html_document
---

## 1 Load Packages
```{r include=FALSE}
library(tidyverse)
library(readxl)
library(ggsci)
library(GGally)

library(car)
library(glmmTMB)
library(effects)
library(emmeans)
library(ggeffects)
library(DHARMa)


library(sf)

main_theme = theme_minimal()+
  theme(line = element_blank(), 
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        axis.ticks =  element_line(colour = "black"),
        axis.text.x = element_text(colour = "black", size=22, face="italic", angle = 45, vjust = 1, hjust = 1),
        axis.text.y = element_text(colour = "black", size=22, face="italic"),
        legend.title = element_text(colour = "black", size=20,
                                    hjust =0.5),

        legend.text = element_text(colour = "black", size=18),
        axis.title= element_text(size=28),
        strip.text = element_text(colour = "black", size=15, face ="italic"))

```

## 2 Arrange data to long format

```{r include=FALSE}
data <- read_xlsx("data/R_PhD_Data_corrected2.xlsx")
data %>% filter(is.na(Shade_tree_Canopy_Cover))
data %>%
  rename(sample_code = "Coffee_soil _sample_CODE") %>%
  mutate(sample_code = paste(sample_code,
                             str_extract(Section_of_Kaweri, "^[a-zA-Z]{4}"), sep = "_"),
         Shade_tree_soil_sample_CODE = paste(Shade_tree_soil_sample_CODE,
                             str_extract(Section_of_Kaweri, "^[a-zA-Z]{4}"), sep = "_")) -> data



covariate_data <- data %>%
  select(Shade_tree_species, Section_of_Kaweri, sample_code, Coffee_Variety,
         Actual_distance_from_shade_tree_m, Shade_tree_soil_sample_CODE) %>% 
  mutate(Coffee_Variety = case_when(is.na(Coffee_Variety) ~"unknown_var",
                                    .default = Coffee_Variety))

 data %>% 
  select(sample_code, starts_with("inc"), starts_with("Inc")) %>%
  pivot_longer(-sample_code, values_to = "value", names_to = "value_type") %>%
  mutate(
    # Extracting "disease" (e.g., "CWD", "CLR", "CRBD")
    disease = str_extract(value_type, "(?<=_)[A-Z]+"),
    
    # Extracting "portion"
    portion = str_extract(value_type, "(?<=_)lower|Top|middle"),
    
    # Extracting "branch" (e.g., "1st", "2nd", "3rd", "4th")
    branch = str_extract(value_type, "\\d+(st|nd|rd|th)"),
    
    # Extracting "value_type" (e.g., "incidence" or "Incidence")
    value_type = str_extract(value_type, "^[^_]+"),
    
    # change "Incidence"  to "incidence")
    value_type = str_replace_all(value_type, "Incidence", "incidence")
  ) %>%
  mutate(value = ifelse(value>=1,1,0 )) %>%
  left_join(covariate_data, by = "sample_code") %>%
  group_by(sample_code, disease) %>% # sample code are the ID to individual coffee tree
  summarise(true_incidence = ifelse(sum(value, na.rm = T)>=1,1,0), # 0 occurrence = 0 ; 1 to 12 occurrence = 1
            n =  n(),
            distance = unique(Actual_distance_from_shade_tree_m),
            Shade_tree_species = unique(Shade_tree_species),
            Shade_tree_soil_sample_CODE = unique(Shade_tree_soil_sample_CODE),
            Coffee_Variety = unique(Coffee_Variety)) %>%
   ungroup() -> data_incidence
```

## 3 Incidence model

### 3.1 CRBD incidence data

#### Shade tree

```{r}
data_incidence %>%
  filter(disease == "CRBD") -> binary_data_CRBD
## Compute binomial glm  
mod_binary_incidence_CRBD <- glm(formula = true_incidence ~ Shade_tree_species*distance + Coffee_Variety,
                              family = binomial,
                              data = binary_data_CRBD)
```


```{r include=FALSE}
res_incidence_CRBD<- DHARMa::simulateResiduals(mod_binary_incidence_CRBD, plot = TRUE)
testDispersion(res_incidence_CRBD)
testZeroInflation(res_incidence_CRBD)
```


```{r echo=FALSE}
summary(mod_binary_incidence_CRBD)

## Anova of type 2 and 3 are more robust that basic anova 
car::Anova(mod_binary_incidence_CRBD, 2) %>%
  round(2) %>%
  knitr::kable()
car::Anova(mod_binary_incidence_CRBD, 3)

predict_response(mod_binary_incidence_CRBD, c("Shade_tree_species"), margin = "marginalmeans") %>%
  plot()

predict_response(mod_binary_incidence_CRBD, c("distance[all]"), margin = "marginalmeans") %>%
  as.data.frame %>%
  ggplot() +
  geom_line(aes(x, predicted), cex =2) +
  scale_y_continuous(limits = c(0,1))+
  main_theme +
  labs(x= "distance", y = "incidence CRBD")
```
No effect (see anova)

### 3.2 CWD incidence data

#### Shade tree

```{r}
data_incidence %>%
  filter(disease == "CWD")  -> binary_data_CWD

## Compute binomial glm  
mod_binary_incidence_CWD <- glm(formula = true_incidence ~ Shade_tree_species*distance + Coffee_Variety,
                              family = binomial,
                              data = binary_data_CWD)
```


```{r include=FALSE}
res_incidence_CWD<- DHARMa::simulateResiduals(mod_binary_incidence_CWD, plot = TRUE)
testDispersion(res_incidence_CWD)
testZeroInflation(res_incidence_CWD)
```


```{r}
## Anova 
car::Anova(mod_binary_incidence_CWD, 2) %>%
  round(2)
car::Anova(mod_binary_incidence_CWD, 3)
summary(mod_binary_incidence_CWD)

binary_data_CWD %>%
  ggplot() +
  geom_bar(aes(Coffee_Variety, fill = as.factor(true_incidence)),position = "fill") +
  labs(y = "Incidence proportion \n CWD", x = "Coffee Variety", fill = "Coffee tree state \n ( 1 infected, 0 not infected)" ) +
  scale_fill_startrek()+
  main_theme

### Pairwise  comparison
pwc_incidence_CWD <- emmeans(mod_binary_incidence_CWD, ~Coffee_Variety, type = "responce")
pairs(pwc_incidence_CWD)
multcomp::cld(pwc_incidence_CWD, Letter = "abcdefg") %>%
  as.data.frame() %>%
  dplyr::select(Coffee_Variety, .group) -> compl_letter 

### Variety
predict_response(mod_binary_incidence_CWD, c("Coffee_Variety"), margin = "marginalmeans") %>% #  margin = "marginalmeans" is to average over all shade tree, ortherwise prediction would be fixe for reference shade tree (albizia)
  as.data.frame %>%
  left_join(compl_letter, by = join_by(x == Coffee_Variety)) %>%
  ggplot() +
  geom_pointrange(aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high,), 
                  linetype =1, cex = 0.5, linewidth = 1, position = position_dodge(width = .2)) +
  geom_text(aes(label = .group, x = x, y = 1), size = 5, vjust = 0) +
  scale_y_continuous(limits = c(0,1))+
  main_theme +
  labs(x= "Variety", y = "incidence CWD") 

predict_response(mod_binary_incidence_CWD, c("distance[all]"), margin = "marginalmeans") %>%
  as.data.frame %>%
  ggplot() +
  geom_line(aes(x, predicted), cex =2) +
  scale_y_continuous(limits = c(0,1))+
  main_theme +
  labs(x= "distance", y = "incidence CWD")
```

```{r}
predict_response(mod_binary_incidence_CWD, c("distance [all]","Shade_tree_species"), type = "fixed") %>%
  as.data.frame %>%
  ggplot() +
  geom_ribbon(aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high), alpha= 0.5 )+
  geom_line(aes(x = x, y = predicted))+
  facet_wrap(~group) +
  scale_y_continuous(limits = c(0,1))+
  main_theme +
  labs(x= "Distance", y = "Incidence probability") 
```


### 3.3 CLR incidence data

#### Shade tree

```{r}
data_incidence %>%
  filter(disease == "CLR") -> binary_data_CLR

## Compute binomial glm  
mod_binary_incidence_CLR <- glm(formula = true_incidence ~ Shade_tree_species*distance + Coffee_Variety, #  (don't work)
                              family = binomial,
                              data = binary_data_CLR)
```


```{r include=FALSE}
res_incidence_CLR<- DHARMa::simulateResiduals(mod_binary_incidence_CLR, plot = TRUE)
testDispersion(res_incidence_CLR)
testZeroInflation(res_incidence_CLR)
```


```{r}
## Anova of type 2 and 3 are more robust that basic anova 
car::Anova(mod_binary_incidence_CLR, 2) %>%
  round(2) %>%
  knitr::kable()
car::Anova(mod_binary_incidence_CLR, 3)

##
summary(mod_binary_incidence_CLR)

predict_response(mod_binary_incidence_CLR, c("distance [all]","Shade_tree_species"), type = "fixed") %>%
  as.data.frame %>%
  ggplot() +
  geom_ribbon(aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high), alpha= 0.5 )+
  geom_line(aes(x = x, y = predicted))+
  facet_wrap(~group) +
  scale_y_continuous(limits = c(0,1))+
  main_theme +
  labs(x= "Distance", y = "Incidence probability") 

pwc_ClR_incid <- emmeans(mod_binary_incidence_CLR, ~Shade_tree_species| distance, component = 'response')


pairs(pwc_ClR_incid)
multcomp::cld(pwc_ClR_incid, Letter = "abcdefg") %>%
  as.data.frame() %>%
  dplyr::select(Shade_tree_species, .group) -> compl_letter 

predict_response(mod_binary_incidence_CLR, c("Shade_tree_species"), type = "fixed") %>%
  as.data.frame %>%
  left_join(compl_letter, by = join_by(x == Shade_tree_species)) %>%
  ggplot() +
  geom_text(aes(label = .group, x = x, y = 1), size = 5, vjust = 0) +
  geom_pointrange(aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high,), 
                  linetype =1, cex = 0.5, linewidth = 1, position = position_dodge(width = .2)) +
  scale_y_continuous(limits = c(0,1.1))+
  main_theme +
  labs(x= "Shade tree", y = "Incidence probability") 

predict_response(mod_binary_incidence_CLR, c("distance[all]"), margin = "marginalmeans") %>%
  as.data.frame %>%
  ggplot() +
  geom_line(aes(x, predicted), cex =2) +
  scale_y_continuous(limits = c(0,1))+
  main_theme +
  labs(x= "distance", y = "incidence CRBD")
```


### 4.4 Recap incidence : graph

```{r}
data_incidence %>%
  ggplot()+
  facet_wrap(~disease) +
  geom_bar(aes(Shade_tree_species, fill = as.factor(true_incidence)), position = "fill") +
  scale_fill_startrek() +
  labs(x = " Shade tree", y = "Proportion", fill = "Incidence") +
  main_theme

data_incidence %>%
  ggplot()+
  facet_wrap(~disease) +
  geom_bar(aes(Coffee_Variety, fill = as.factor(true_incidence)), position = "fill") +
  scale_fill_startrek() +
  labs(x = " Coffee Variety", y = "Proportion", fill = "Incidence") +
  main_theme
```



## 4 Severity model

### 4.1 Compute severity for each branchs

```{r include=FALSE}
### Isolate total cont of leaves or berries per branch
data %>%
  select(sample_code, starts_with("No_berries"),  starts_with("No_leaves")) %>%
  pivot_longer(-sample_code, names_to = "sample_type", values_to = "total_count") %>%
  mutate(
    # Extracting "organ" ("berries" or "leaves")
    organ = str_extract(sample_type, "(?<=_)berries|leaves"),
    
    # Extracting "portion"
    portion = str_extract(sample_type, "(?<=_)lower|Top|middle"),
    
    # Extracting "branch" (e.g., "1st", "2nd", "3rd", "4th")
    branch = str_extract(sample_type, "\\d+(st|nd|rd|th)")
   ) %>%
  select(-sample_type) -> total_number_of_leaves_or_berries

### Isolate total count of leaves or berries infected per branchs
data %>%
  select(sample_code, starts_with("No"),  -starts_with("No_berries"),  -starts_with("No_leaves")) %>% # extract the total number of leaves/berries and the number of leaves/berries infected
  pivot_longer(-sample_code, names_to = "sample_type", values_to = "infected_count") %>%
  mutate(
     # Extracting "disease" (e.g., "CWD", "CLR", "CRBD")
    disease = str_extract(sample_type, "(?<=_)[A-Z]+"),
    
    # Extracting "organ" ("berries" or "leaves")
    organ = str_extract(sample_type, "(?<=_)berries|leaves"),
    
    # Extracting "portion"
    portion = str_extract(sample_type, "(?<=_)lower|Top|middle"),
    
    # Extracting "branch" (e.g., "1st", "2nd", "3rd", "4th")
    branch = str_extract(sample_type, "\\d+(st|nd|rd|th)")
   ) -> number_of_infected_leaves_or_berries

## Merge data and compute serverity per branchs
number_of_infected_leaves_or_berries %>%
  left_join(total_number_of_leaves_or_berries, by = join_by("sample_code" == "sample_code",
                                                            "branch" == "branch",
                                                            "portion" == "portion",
                                                            "organ" == "organ")) %>%
  mutate(severity = infected_count/total_count) %>%
  left_join(covariate_data, by = "sample_code") %>%
  mutate(Shade_tree_species = as.factor(Shade_tree_species)) %>%
  rename(distance = "Actual_distance_from_shade_tree_m") %>%
  mutate(distance_class = cut(
      distance,
      breaks = c(0, 8, 16, 24),  # Specify the breakpoints
      labels = c("[0-8]", "(8-16]", "(16-22]"),  # Labels for each range
      right = F), # Indicates whether intervals are right-closed
    total_count = case_when(total_count > 250 ~ round(total_count/10),
                            .default = total_count),
    log_total_count = log(total_count), # correct error (5 branch have more than 150 leaves -> error due to one digit added when tipping)
    across(where(is.character),~as.factor(.x))) -> data_severity
```
 
 Function to compute models for all disease at each 3 portions of coffee tree.
 
```{r echo=FALSE}
data_severity %>%
  filter(organ != "berries",
         (portion == "Top" & disease %in% c("CRBD", "CWD")) |  portion == "lower" & disease == "CLR") %>%
  dplyr::select(severity, sample_code, disease,branch) -> disease_corr_df

disease_corr_df %>%
  pivot_wider(names_from = disease, values_from = severity) %>% 
  dplyr::select(CWD, CLR, CRBD) %>%
  rename(CWD_top = "CWD", CLR_low = "CLR", CRBD_top = "CRBD")%>%
  ggpairs() +
  theme_bw()+
  theme(line = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.ticks =  element_line(colour = "black"),
        axis.text.x = element_text(colour = "black", size=22, face="italic", angle = 45, vjust = 1, hjust = 1),
        axis.text.y = element_text(colour = "black", size=22, face="italic"),
        axis.title= element_text(size=20),
        strip.text = element_text(colour = "black", size=10, face ="italic"))

disease_corr_df %>%
  filter(severity != 0) %>%
  pivot_wider(names_from = disease, values_from = severity) %>%
  dplyr::select(CWD, CLR, CRBD) %>%
  rename(CWD_top = "CWD", CLR_low = "CLR", CRBD_top = "CRBD")%>%
  ggpairs() +
  theme_bw()+
  theme(line = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.ticks =  element_line(colour = "black"),
        axis.text.x = element_text(colour = "black", size=22, face="italic", angle = 45, vjust = 1, hjust = 1),
        axis.text.y = element_text(colour = "black", size=22, face="italic"),
        axis.title= element_text(size=20),
        strip.text = element_text(colour = "black", size=10, face ="italic"))
```
 
```{r include=FALSE}

severity.mod.func <- function(data, 
                              frml,
                              zifrml,
                              disprml = formula("~1")){
 
  mod_severity <-  glmmTMB(formula = frml,
                              ziformula = zifrml,
                              dispformula = disprml,
                              family = beta_family(),
                              #weights = total_count ,
                              data = data)

  res_severity <- DHARMa::simulateResiduals(mod_severity, plot = TRUE)


  par(mfrow = c(2, 3))
  testDispersion(res_severity)
  testZeroInflation(res_severity)
  plotResiduals(res_severity, form = data$distance )
  plotResiduals(res_severity, form = data$Shade_tree_species)
  plotResiduals(res_severity, form = data$log_total_count)
  plotResiduals(res_severity, form = data$Coffee_Variety)
  par(mfrow = c(1, 1))
  
  return(mod_severity)
}

```

### 4.2 CRBD LEAVES severity model

```{r include=FALSE}
data_severity %>%
  filter(disease == "CRBD", organ =="leaves") -> data_severity_CRBD_leaves
```

#### Top portion

```{r results = 'hide'}
# Models
data_severity_CRBD_leaves %>%
  filter(portion =="Top", !is.na(severity)) %>%
  mutate(severity = case_when(severity == 1 ~ severity*0.999,
                              .default = severity))-> CRBD_leaves_top

CRBD_leaves_top%>%
  severity.mod.func(frml = formula("severity ~ Shade_tree_species *distance   + (1|Section_of_Kaweri)"),
                    zifrml = formula("~1")) -> mod_severity_CRBD_leaves_top

CRBD_leaves_top%>%
  severity.mod.func(frml = formula("severity ~ Shade_tree_species*distance   + Coffee_Variety +
                                            (1|Section_of_Kaweri)"),
                    zifrml = formula("~1")) -> mod_severity_CRBD_leaves_top2
CRBD_leaves_top%>%
  severity.mod.func(frml = formula("severity ~ Shade_tree_species*distance   + Coffee_Variety +
                                            (1|Section_of_Kaweri)"),
                              zifrml = formula("~Coffee_Variety")) -> mod_severity_CRBD_leaves_top3
CRBD_leaves_top%>%
  severity.mod.func(frml = formula("severity ~ Shade_tree_species*distance   + 
                                            (1|Section_of_Kaweri)"),
                              zifrml = formula("~Coffee_Variety ")) -> mod_severity_CRBD_leaves_top4

CRBD_leaves_top%>%
  severity.mod.func(frml = formula("severity ~ Shade_tree_species*distance   +
                                            (1|Section_of_Kaweri)"),
                    zifrml = formula("~Coffee_Variety"),
                    disprml = formula("~Coffee_Variety")) -> mod_severity_CRBD_leaves_top5

```



```{r}

# Anova
Anova(mod_severity_CRBD_leaves_top5) %>%
  round(2) %>%
  knitr::kable()

Anova(mod_severity_CRBD_leaves_top5, component = "zi") %>%
  knitr::kable()

Anova(mod_severity_CRBD_leaves_top5, component = "disp") %>%
  knitr::kable()

### Pairwise comparison variety
pwc_CRBD <- emmeans(mod_severity_CRBD_leaves_top5, ~Coffee_Variety, component = 'response')
summary(pwc_CRBD)

pairs(pwc_CRBD)
multcomp::cld(pwc_CRBD, Letter = "abcdefg") %>%
  as.data.frame() %>%
  dplyr::select(Coffee_Variety, .group) -> compl_letter 

### Variety
predict_response(mod_severity_CRBD_leaves_top5, c("Coffee_Variety"), type = "zero_inflated") %>% 
  as.data.frame %>%
  left_join(compl_letter, by = join_by(x == Coffee_Variety)) %>%
  mutate(x = factor(x, level = compl_letter$Coffee_Variety)) %>%
  ggplot() +
  geom_pointrange(aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high,), 
                  linetype =1, cex = 0.5, linewidth = 1, position = position_dodge(width = .2)) +
  geom_text(aes(label = .group, x = x, y = 0.2), size = 5, vjust = 0) +
  scale_y_continuous(limits = c(0,0.25))+
  main_theme +
  labs(x= "Variety", y = "severity CRBD") 

### Distance
predict_response(mod_severity_CRBD_leaves_top5, c("distance[all]"), type = "fixed", margin = "marginalmeans") %>%
  as.data.frame %>%
  ggplot() +
  geom_ribbon(aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high), alpha= 0.5) +
  geom_line(aes(x = x, y = predicted)) +
  scale_y_continuous(limits = c(0,0.5)) +
  labs(x = "Distance", y= "CRBD severity") +
  main_theme
```

### 4.3 CWD severity model

```{r include=FALSE}
data_severity %>%
  filter(disease == "CWD") -> data_severity_CWD
```

#### Top

```{r results = 'hide'}
# Models

data_severity_CWD %>%
  filter(portion =="Top", !is.na(severity)) %>%
  mutate(severity = case_when(severity == 1 ~ severity*0.999,
                              .default = severity))-> CWD_top
nrow(CWD_top)
CWD_top%>%
  severity.mod.func(frml = formula("severity ~ Shade_tree_species*distance + 
                                            (1|Section_of_Kaweri)"),
                    zifrml =  formula("~1")) -> mod_severity_CWD_top

CWD_top%>%
  severity.mod.func(frml = formula("severity ~ Shade_tree_species*distance   + Coffee_Variety + 
                                            (1|Section_of_Kaweri)"),
                     zifrml =  formula("~1")) -> mod_severity_CWD_top2
CWD_top%>%
  severity.mod.func(frml = formula("severity ~ Shade_tree_species*distance   + Coffee_Variety + 
                                            (1|Section_of_Kaweri)"),
                              zifrml = formula("~Coffee_Variety")) -> mod_severity_CWD_top3

CWD_top%>%
  severity.mod.func(frml = formula("severity ~ Shade_tree_species*distance  + 
                                            (1|Section_of_Kaweri)"),
                              zifrml = formula("~Coffee_Variety")) -> mod_severity_CWD_top4
CWD_top%>%
  severity.mod.func(frml = formula("severity ~ Shade_tree_species*distance  + 
                                            (1|Section_of_Kaweri)"),
                              zifrml = formula("~Shade_tree_species")) -> mod_severity_CWD_top5

```

```{r}
# Select model
AIC(mod_severity_CWD_top, mod_severity_CWD_top3, mod_severity_CWD_top4,mod_severity_CWD_top5) %>%
  round(1) %>%
  knitr::kable()

# Anova Model 1
Anova(mod_severity_CWD_top) %>%
  round(2) %>%
  knitr::kable()
Anova(mod_severity_CWD_top,component = "zi") %>%
  round(2)
Anova(mod_severity_CWD_top, "III")%>%
  round(2)

# Anova Model 5
Anova(mod_severity_CWD_top5) %>%
  round(2)
Anova(mod_severity_CWD_top5,component = "zi") %>%
  round(2)
Anova(mod_severity_CWD_top5, "III") %>%
  round(2)

summary(mod_severity_CWD_top)

# Distance
predict_response(mod_severity_CWD_top, c("distance[all]"), type = "fixed", margin = "marginalmeans") %>%
  as.data.frame %>%
  ggplot() +
  geom_ribbon(aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high), alpha= 0.5) +
  geom_line(aes(x = x, y = predicted)) +
  scale_y_continuous(limits = c(0,0.5)) +
  labs(x = "Distance", y= "CWD severity") +
  main_theme
```

### 5.5 CLR severity model

```{r include=FALSE}
data_severity %>%
  filter(disease == "CLR") -> data_severity_CLR
```
#### Low

```{r results = 'hide'}
# Models
data_severity_CLR %>%
  filter(portion == "lower", !is.na(severity)) %>%
  mutate(severity = case_when(severity == 1 ~ severity*0.999,
                              .default = severity)) -> CLR_low

CLR_low %>%
 severity.mod.func(frml = formula("severity ~ Shade_tree_species*distance + 
                                            (1|Section_of_Kaweri)"),
                   zifrml =  formula("~1")) -> mod_severity_CLR_low
CLR_low %>%
 severity.mod.func(frml = formula("severity ~ Shade_tree_species*distance   + Coffee_Variety + 
                                            (1|Section_of_Kaweri)"),
                   zifrml = formula("~1")) -> mod_severity_CLR_low2
CLR_low %>%
 severity.mod.func(frml = formula("severity ~ Shade_tree_species*distance    + Coffee_Variety+
                                            (1|Section_of_Kaweri)"),
                   zifrml = formula("~Coffee_Variety")) -> mod_severity_CLR_low3
CLR_low %>%
 severity.mod.func(frml = formula("severity ~ Shade_tree_species*distance    + 
                                            (1|Section_of_Kaweri)"),
                   zifrml = formula("~Coffee_Variety")) -> mod_severity_CLR_low4

CLR_low%>%
  severity.mod.func(frml = formula("severity ~ Shade_tree_species*distance  + 
                                            (1|Section_of_Kaweri)"),
                    zifrml = formula("~Shade_tree_species")) -> mod_severity_CLR_low5
CLR_low%>%
  severity.mod.func(frml = formula("severity ~ Shade_tree_species*distance  + Coffee_Variety+
                                            (1|Section_of_Kaweri)"),
                    zifrml = formula("~Shade_tree_species")) -> mod_severity_CLR_low6

CLR_low %>%
 severity.mod.func(frml = formula("severity ~ Shade_tree_species*distance    + Coffee_Variety +
                                            (1|Section_of_Kaweri)"),
                    zifrml = formula("~Coffee_Variety"),
                    disprml =formula("~Coffee_Variety") ) -> mod_severity_CLR_low7
CLR_low %>%
 severity.mod.func(frml = formula("severity ~ Shade_tree_species*distance     +
                                            (1|Section_of_Kaweri)"),
                    zifrml = formula("~1"),
                    disprml =formula("~Coffee_Variety") ) -> mod_severity_CLR_low8

CLR_low %>%
 severity.mod.func(frml = formula("severity ~ Shade_tree_species*distance    +Coffee_Variety*distance+
                                            (1|Section_of_Kaweri)"),
                    zifrml = formula("~Coffee_Variety"),
                    disprml =formula("~log_total_count") ) -> mod_severity_CLR_low9
CLR_low %>%
 severity.mod.func(frml = formula("severity ~ Shade_tree_species*distance    +Coffee_Variety*distance+
                                            (1|Section_of_Kaweri)"),
                    zifrml = formula("~Coffee_Variety"),
                    disprml =formula("~log_total_count + Coffee_Variety") ) -> mod_severity_CLR_low10
CLR_low %>%
 severity.mod.func(frml = formula("severity ~ Shade_tree_species*distance    + Coffee_Variety*distance+ 
                                            (1|Section_of_Kaweri)"),
                    zifrml = formula("~Coffee_Variety*distance"),
                    disprml =formula("~Coffee_Variety*distance") ) -> mod_severity_CLR_low11


```


```{r}
# Anova
Anova(mod_severity_CLR_low10) %>%
  round(2) %>%
  knitr::kable()
Anova(mod_severity_CLR_low10,3)

Anova(mod_severity_CLR_low10,component = "zi") %>%
  round(2) %>%
  knitr::kable()
Anova(mod_severity_CLR_low10,component = "disp") %>%
  round(2) %>%
  knitr::kable()

summary(mod_severity_CLR_low10)

## Zero inflation
### Pairwise comparison variety
pwc_CLR_zi <- emmeans(mod_severity_CLR_low10, ~Coffee_Variety, component = 'zi')
pairs(pwc_CLR_zi)
multcomp::cld(pwc_CLR_zi, Letter = "abcdefg") %>%
  as.data.frame() %>%
  dplyr::select(Coffee_Variety, .group) -> compl_letter_zi 

### Variety
predict_response(mod_severity_CLR_low10, c("Coffee_Variety"), type = "zi_prob") %>%
  as.data.frame %>%
  left_join(compl_letter_zi, by = join_by(x == Coffee_Variety)) %>%
  mutate(x = factor(x, level = compl_letter_zi$Coffee_Variety)) %>%
  ggplot() +
  geom_pointrange(aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high,), 
                  linetype =1, cex = 0.5, linewidth = 1, position = position_dodge(width = .2)) +
  geom_text(aes(label = .group, x = x, y = 0.5), size = 5, vjust = 0) +
  scale_y_continuous(limits = c(0,0.5))+
  main_theme +
  labs(x= "Variety", y = "severity CLR") 

## Fixed effect
### Pairwise comparison variety
pwc_CLR_fixed <- emmeans(mod_severity_CLR_low10, ~Coffee_Variety|distance, component = 'cond')
pairs(pwc_CLR_fixed)
multcomp::cld(pwc_CLR_fixed, Letter = "abcdefg") %>%
  as.data.frame() %>%
  dplyr::select(Coffee_Variety, .group) -> compl_letter_fixed

### Variety
predict_response(mod_severity_CLR_low10, c("Coffee_Variety"), type = "fixed") %>%
  as.data.frame %>%
  left_join(compl_letter_fixed, by = join_by(x == Coffee_Variety)) %>%
  mutate(x = factor(x, level = compl_letter_fixed$Coffee_Variety)) %>%
  ggplot() +
  geom_pointrange(aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high,), 
                  linetype =1, cex = 0.5, linewidth = 1, position = position_dodge(width = .2)) +
  geom_text(aes(label = .group, x = x, y = 0.5), size = 5, vjust = 0) +
  scale_y_continuous(limits = c(0,0.5))+
  main_theme +
  labs(x= "Variety", y = "severity CLR") 

## response
pwc_CLR <- emmeans(mod_severity_CLR_low10, ~Coffee_Variety|distance, component = 'response')
pairs(pwc_CLR)
multcomp::cld(pwc_CLR, Letter = "abcdefg") %>%
  as.data.frame() %>%
  dplyr::select(Coffee_Variety, .group) -> compl_letter 

### Variety
predict_response(mod_severity_CLR_low10, c("Coffee_Variety"), type = "zero_inflated") %>%
  as.data.frame %>%
  left_join(compl_letter, by = join_by(x == Coffee_Variety)) %>%
  mutate(x = factor(x, level = compl_letter$Coffee_Variety)) %>%
  ggplot() +
  geom_pointrange(aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high,), 
                  linetype =1, cex = 0.5, linewidth = 1, position = position_dodge(width = .2)) +
  geom_text(aes(label = .group, x = x, y = 0.5), size = 5, vjust = 0) +
  scale_y_continuous(limits = c(0,0.5))+
  main_theme +
  labs(x= "Variety", y = "severity CLR") 

### variety interaction distance (partial effect of distance and Coffee_Variety)

emtrends(mod_severity_CLR_low10, pairwise ~ Coffee_Variety, var = "distance")
emmip(mod_severity_CLR_low10, Coffee_Variety ~ distance, cov.reduce = range)

predict_response(mod_severity_CLR_low10, c("distance [all]", "Coffee_Variety"), type = "fixed") %>%
  as.data.frame %>%
  ggplot() +
    facet_wrap(~group)+
  geom_ribbon(aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high), alpha= 0.5) +

  geom_line(aes(x = x, y = predicted)) +
  scale_y_continuous(limits = c(0,1)) +
  labs(x = "Distance", y= "CLR severity") +
  main_theme

##
### Distance
predict_response(mod_severity_CLR_low10, c("distance[all]"),  type = "fixed", margin = "marginalmeans") %>%
  as.data.frame %>%
  ggplot() +
 
  geom_ribbon(aes(x = x, y = predicted, ymin = conf.low, ymax = conf.high), alpha= 0.5) +

  geom_line(aes(x = x, y = predicted)) +
  scale_y_continuous(limits = c(0,0.4)) +
  labs(x = "Distance", y= "CLR severity") +
  main_theme
```