---
title: "clean_yield_models"
output: html_document
date: "2025-01-24"
editor_options: 
  chunk_output_type: inline
---
# Setup data and packages(no shown)
## 1 Load Packages
```{r  include=FALSE}
library(tidyverse)
library(readxl)
library(GGally)
library(viridis)
library(ggsci)
library(patchwork)

library(glmmTMB)
library(DHARMa)
library(car)
library(modelbased)
library(performance)



main_theme = theme_minimal()+
  theme(line = element_blank(), 
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        axis.ticks =  element_line(colour = "black"),
        axis.text.x = element_text(colour = "black", size=22, face="italic", angle = 45, vjust = 1, hjust = 1),
        axis.text.y = element_text(colour = "black", size=22, face="italic"),
        legend.title = element_text(colour = "black", size=20,
                                    hjust =0.5),

        legend.text = element_text(colour = "black", size=18),
        axis.title= element_text(size=28),
        strip.text = element_text(colour = "black", size=15, face ="italic"))
```

Function to convert GPS point to decimal degrees


```{r include=FALSE}
convert_dms_to_dd <- function(dms) {
  if(is.na(dms)){
    return(NA)
  }
  if(str_detect(dms, "^\\d+$")){
    return(NA)
  } else{
  dms <- str_replace_all(dms, "[°′″’']", " ") # Replace degree, minute, and second symbols with spaces
  dms_split <- str_split(dms, "\\s+")[[1]]  # Split the string into components
  degrees <- as.numeric(dms_split[1])
  minutes <- as.numeric(dms_split[2])
  seconds <- as.numeric(dms_split[3])
  direction <- dms_split[4]
  
  # Calculate decimal degrees
  decimal_degrees <- degrees + minutes / 60 + seconds / 3600
  if (direction %in% c("S", "W")) {
    decimal_degrees <- -decimal_degrees
  }
  return(decimal_degrees)
  }
}
```

## 2 Arrange data to long format

```{r include=FALSE}
data <- read_xlsx("data/R_PhD_Data_corrected2.xlsx")

data %>% filter(is.na(Shade_tree_Canopy_Cover))
data %>%
  rename(sample_code = "Coffee_soil _sample_CODE") %>%
  # change sample_code names
  mutate(sample_code = paste(sample_code,
                             str_extract(Section_of_Kaweri, "^[a-zA-Z]{4}"), sep = "_"),
         Shade_tree_soil_sample_CODE = paste(Shade_tree_soil_sample_CODE,
                             str_extract(Section_of_Kaweri, "^[a-zA-Z]{4}"), sep = "_")) %>%
   mutate(Shade_tree_species = case_when(Shade_tree_species == "Ficus natalensis"~ "Fn",
                                        Shade_tree_species == "Albizia coriaria" ~ "Ac",
                                        Shade_tree_species == "Artocarpus heterophyllus" ~ "Ah",
                                        Shade_tree_species == "Persea americana" ~ "Pa")) -> data
data %>%
  select(Shade_tree_species, Section_of_Kaweri, sample_code, 
       Coffee_Variety, Actual_distance_from_shade_tree_m, 
       Shade_tree_Canopy_Cover, Shade_tree_soil_sample_CODE,
       Longitude, Latitude) %>%
  mutate(Coffee_Variety = case_when(Coffee_Variety== "Unidentified" ~"Op2",
                                    Coffee_Variety== "Open pollinated" ~"Op1",
                                    .default = Coffee_Variety)) %>%
 
  group_by(Shade_tree_soil_sample_CODE) %>%
  mutate(Shade_tree_Canopy_Cover = mean(Shade_tree_Canopy_Cover, na.rm = T),  ## A little trick to replace NA from Shade_tree_Canopy_Cover to good value
          Longitude = ifelse(is.na(Longitude), first(na.omit(Longitude)), Longitude),
          Latitude = ifelse(is.na(Latitude), first(na.omit(Latitude)), Latitude),
          Longitude_dd = ifelse(!is.na(Longitude), sapply(Longitude, convert_dms_to_dd), NA),
          Latitude_dd = ifelse(!is.na(Latitude), sapply(Latitude, convert_dms_to_dd), NA),
          Coffee_Variety = as.factor(Coffee_Variety),
          Shade_tree_species = as.factor(Shade_tree_species),
          distance_class = cut(
          Actual_distance_from_shade_tree_m,
          breaks = c(0, 8, 16, 24),  # Specify the breakpoints
          labels = c("[0-8]", "(8-16]", "(16-22]"),  # Labels for each range
          right = F) # Indicates whether intervals are right-closed
              ) %>%
  
  ungroup() -> covariate_data

```


```{r include=FALSE}
### Isolate total cont of leaves or berries per branch
data %>%
  select(sample_code, starts_with("No_berries"),  starts_with("No_leaves")) %>%
  pivot_longer(-sample_code, names_to = "sample_type", values_to = "total_count") %>%
  mutate(
    # Extracting "organ" ("berries" or "leaves")
    organ = str_extract(sample_type, "(?<=_)berries|leaves"),
    
    # Extracting "portion"
    portion = str_extract(sample_type, "(?<=_)lower|Top|middle"),
    
    # Extracting "branch" (e.g., "1st", "2nd", "3rd", "4th")
    branch = str_extract(sample_type, "\\d+(st|nd|rd|th)")
   ) %>%
  select(-sample_type) %>%
  mutate(total_count = case_when(total_count > 250 & organ == "leaves" ~ round(total_count/10),
                            .default = total_count)) %>%  # correct error (5 branch have more than 250 leaves -> error due to one digit added when tipping)
  pivot_wider(names_from = organ, values_from = total_count ) %>%
  group_by(sample_code) %>%
  summarise(berries = sum(berries, na.rm =T),
            leaves = sum(leaves, na.rm =T)) -> total_number_of_leaves_or_berries

### Isolate total count of leaves or berries infected per branchs
data %>%
  select(sample_code, starts_with("No"),  -starts_with("No_berries"),  -starts_with("No_leaves")) %>% # extract colums of total number of leaves/berries and number of leaves/berries infected
  pivot_longer(-sample_code, names_to = "sample_type", values_to = "infected_count") %>%
  mutate(
     # Extracting "disease" (e.g., "CWD", "CLR", "CRBD")
    disease = str_extract(sample_type, "(?<=_)[A-Z]+"),
    
    # Extracting "organ" ("berries" or "leaves")
    organ = str_extract(sample_type, "(?<=_)berries|leaves"),
    
    # Extracting "portion"
    portion = str_extract(sample_type, "(?<=_)lower|Top|middle"),
    
    # Extracting "branch" (e.g., "1st", "2nd", "3rd", "4th")
    branch = str_extract(sample_type, "\\d+(st|nd|rd|th)")
   ) %>%
  select(-sample_type) %>%
  pivot_wider(names_from = c(disease,organ),
              names_glue = "{disease}_infected_{organ}",
              values_from = infected_count  ) %>%
  group_by(sample_code) %>%
  # number of infected leaves and berries per shrubs and disease
  summarise(CWD_infected_leaves = sum(CWD_infected_leaves, na.rm =T),
            CLR_infected_leaves = sum(CLR_infected_leaves, na.rm =T),
            CRBD_infected_leaves = sum(CRBD_infected_leaves, na.rm =T),
            CRBD_infected_berries = sum(CRBD_infected_berries, na.rm =T)) -> number_of_infected_leaves_or_berries


## Merge data and compute leaf_incidence per branchs
number_of_infected_leaves_or_berries %>%
  left_join(total_number_of_leaves_or_berries, by = join_by("sample_code" == "sample_code")) %>%
  left_join(covariate_data, by = "sample_code") %>%
  mutate(Shade_tree_species = as.factor(Shade_tree_species)) %>%
  rename(distance = "Actual_distance_from_shade_tree_m")%>%
  mutate(berries = as.integer(berries),
         leaves = as.integer(leaves),
         )%>%
  mutate(CWD_leaf_incidence = CWD_infected_leaves/leaves,
            CLR_leaf_incidence = CLR_infected_leaves/leaves,
            CRBD_leaf_incidence = CRBD_infected_leaves/leaves,
            CRBD_leaf_incidence_berries = CRBD_infected_berries/(berries+1)) -> data_yield

##Remove shrubs with no leaves (dead shrub). Remove all Clone H and D
data_yield %>%
  filter(leaves != 0) %>%
  filter(!(Coffee_Variety %in% c("Clone H", "Clone D"))) %>%
  mutate(Coffee_Variety  = as.factor(as.character(Coffee_Variety)),
         Shade_tree_soil_sample_CODE = as.factor(Shade_tree_soil_sample_CODE),
         Section_of_Kaweri = as.factor(Section_of_Kaweri),
         log_total_count = log(leaves))-> data_yield2

str(data_yield2)
```

# Yield (nbr berries per tree) explain with **leaf_incidence** 

## Function of residuals check for models

```{r include=FALSE}
# Create a function that take input for a glmm creation. Give back the model and residuals informations.
yield.mod.func2 <- function(data_df, 
                              frml, # Formula for fixed effect of the models
                              fam = gaussian(), # Residuals the models
                              zifrml = "~0", # Formula for zero inflation of the models
                              dispfrml = "~1"){ # Formula for dispersion of the models
  
  # Model creation
  mod_yield <-  glmmTMB(formula = formula(frml),
                              family = fam,
                              ziformula = formula(zifrml),
                              #dispformula = formula(dispfrml),
                              data = data_df)
  # Compute residuals
  res_yeilds <- DHARMa::simulateResiduals(mod_yield, plot = F)
  # Plot to check the choice of residuals family and the homoscedasticity 
  plot(res_yeilds, quantreg = T)
  
  # Plot to check if dispersion term or zero inflation term is needed
  par(mfrow = c(1, 2))
  testDispersion(res_yeilds)
  testZeroInflation(res_yeilds)
  
  # Plot residuals against some variables
  par(mfrow = c(2, 3))
  plotResiduals(res_yeilds, form = data_df$CRBD_infected_berries, quantreg = T)
  plotResiduals(res_yeilds, form = data_df$distance, quantreg = T)
  plotResiduals(res_yeilds, form = data_df$Shade_tree_species)
  plotResiduals(res_yeilds, form = data_df$Coffee_Variety)
  plotResiduals(res_yeilds, form = data_df$Section_of_Kaweri)
  plotResiduals(res_yeilds, form = data_df$log_total_count)
  par(mfrow = c(2, 2))
  
  # Plot residuals against diseases leaf incidence
  plotResiduals(res_yeilds, form = data_df$CLR_leaf_incidence, quantreg = T)
  plotResiduals(res_yeilds, form = data_df$CWD_leaf_incidence, quantreg = T)
  plotResiduals(res_yeilds, form = data_df$CRBD_leaf_incidence, quantreg = T)
  return(mod_yield)
}
```

## Select a model based on residuals

Try different model, the only constrain is that we keep "distance*Shade_tree_species + (1|Shade_tree_soil_sample_CODE)" .
"distance*Shade_tree_species" : are main effect and interaction in which we are interested 
"Shade_tree_soil_sample_CODE" : mixte effect to correct autocorrelation at the shade tree level. Because number of berries per shrubs might be similar around a shade tree due to variable that act locally and that we don't control.

```{r echo = T, results = 'hide'}
data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield
data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + Coffee_Variety +
                    (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield2
data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + Coffee_Variety +Section_of_Kaweri +
                    (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield3

data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + distance*Coffee_Variety + Section_of_Kaweri  +
                    (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield4
data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + distance*Coffee_Variety + Section_of_Kaweri  +
                     (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield5

data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + distance*Coffee_Variety + Section_of_Kaweri + 
                    CLR_leaf_incidence +
                     (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield6
data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + distance*Coffee_Variety + Section_of_Kaweri + 
                    CLR_leaf_incidence + CRBD_leaf_incidence + 
                    (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield7
data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + distance*Coffee_Variety + Section_of_Kaweri + 
                    CLR_leaf_incidence + CRBD_leaf_incidence + log_total_count +
                    (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield7_bis
data_yield2 %>%
  yield.mod.func2(frml = " berries ~ distance * Shade_tree_species + distance * Coffee_Variety +  
    Section_of_Kaweri + CLR_leaf_incidence + CRBD_leaf_incidence + CWD_leaf_incidence + (1 | Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield8
data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + distance*Coffee_Variety + Section_of_Kaweri + 
                    (CLR_leaf_incidence + CRBD_leaf_incidence + CWD_leaf_incidence)^2 +
                    (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield9
data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + distance*Coffee_Variety + Section_of_Kaweri + 
                    CLR_leaf_incidence * CRBD_leaf_incidence * CWD_leaf_incidence +
                    (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield10
data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + distance*Coffee_Variety + Section_of_Kaweri + 
                    (CLR_leaf_incidence + CRBD_leaf_incidence +CWD_leaf_incidence )*Coffee_Variety+
                    (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield12

data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + distance*Coffee_Variety + Section_of_Kaweri + 
                    (CLR_leaf_incidence + CRBD_leaf_incidence )*Coffee_Variety +CWD_leaf_incidence+
                    (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield13

```


## Model selection

Select best model (across model with good residuals) based on AIC

```{r}
AIC(mod_yield,
    mod_yield2,
    mod_yield3,
    mod_yield4,
    mod_yield5,
    mod_yield6,
    mod_yield7,
    mod_yield7_bis,
    mod_yield8,
    mod_yield9,
    mod_yield10
    ,mod_yield13) %>%
  arrange(AIC)
```


```{r}
Anova(mod_yield13) %>% round(2)
```

## Model prediction

### Slope comparison

#### Distance and interaction

```{r}
### Estimate slope values for distance, distance*Shade_tree_species and distance*Coffee_Variety
modelbased::estimate_slopes(mod_yield13,trend = "distance", by = "Shade_tree_species")  %>%
  as.data.frame %>%
  rename(factors = "Shade_tree_species") %>%
  mutate(type = "Shade tree : Distance") -> yield_trend_shade

modelbased::estimate_slopes(mod_yield13, trend = "distance", by = "Coffee_Variety") %>%
  as.data.frame %>%
  rename(factors = "Coffee_Variety") %>%
  mutate(type = "Coffee variety : Distance") -> yield_trend_var

modelbased::estimate_slopes(mod_yield13, trend = "distance") %>%
  as.data.frame %>%
  mutate(type = "Distance alone",
         factors ="Distance") -> yield_trend

### Estimate merge and plot slope values
yield_trend_shade %>%
  bind_rows(yield_trend_var) %>%
  bind_rows(yield_trend) %>%
  mutate(factors = factor(factors, levels = c(as.character(yield_trend_shade$factors),
                                           as.character(yield_trend_var$factors),
                                           as.character(yield_trend$factors))),
         type = factor(type, levels = c("Distance alone",
                                        "Coffee variety : Distance",
                                        "Shade tree : Distance"))) %>%
  ggplot() +
    geom_hline(aes(yintercept = factors), cex =0.2, linetype = 1, color = "gray", alpha =0.2) +
    geom_pointrange(aes(y = factors, x = Slope, xmin = CI_low, xmax = CI_high, colour = type),cex = 0.7, linewidth = 1) +
    geom_vline(xintercept = 0, cex = 1, linetype = 3, color = "red") +
    #facet_grid(rows = vars(type), scales = "free_y")+
 labs(x= "Estimated slopes for fruit load", y = "Slopes types", col = "Predictors")+
    scale_color_brewer(palette = "Set1") +
    theme_classic()+
    theme(aspect.ratio = 1,
          axis.text.x = element_text(colour = "black", size=13, face="italic", angle = 18, vjust =1, hjust =1),
          axis.text.y = element_text(colour = "black", size=13, face="italic"),
          axis.title = element_text(colour = "black", size=16, face ="bold"),
          panel.border = element_rect(colour = "black", fill = NA, linewidth = 1),
          legend.title = element_text(colour = "black", size=16,
                                      hjust =0.5),
  
          legend.text = element_text(colour = "black", size=13)) -> p_yield_trend

p_yield_trend
```


#### Disease and interaction

```{r}
### Estimate slope values for severities and  severities*Coffee_Variety
modelbased::estimate_slopes(mod_yield13, trend = "CLR_leaf_incidence", by = "Coffee_Variety") %>%
  as.data.frame %>%
  rename(factors = "Coffee_Variety") %>%
  mutate(type = "Coffee variety : CLR leaf incidence") -> yield_trend_CLR_var

modelbased::estimate_slopes(mod_yield13, trend = "CRBD_leaf_incidence", by = "Coffee_Variety") %>%
  as.data.frame %>%
  rename(factors = "Coffee_Variety") %>%
  mutate(type = "Coffee variety : BES leaf incidence") -> yield_trend_CRBD_var

modelbased::estimate_slopes(mod_yield13, trend = "CLR_leaf_incidence") %>%
  as.data.frame %>%
  mutate(type = "Disease leaf incidence alone",
         factors ="CLR") -> yield_trend_CLR
modelbased::estimate_slopes(mod_yield13, trend = "CWD_leaf_incidence") %>%
  as.data.frame %>%
  mutate(type = "Disease leaf incidence alone",
         factors ="CWD") -> yield_trend_CWD
modelbased::estimate_slopes(mod_yield13, trend = "CRBD_leaf_incidence") %>%
  as.data.frame %>%
  mutate(type = "Disease leaf incidence alone",
         factors ="BES") -> yield_trend_BES

yield_trend_CLR_var %>%
  bind_rows(yield_trend_CRBD_var) %>%
  bind_rows(yield_trend_CLR) %>%
  bind_rows(yield_trend_CWD) %>%
  bind_rows(yield_trend_BES) %>%
  mutate(factors = factor(factors, levels = c(as.character(yield_trend_CLR_var$factors),
                                              as.character(yield_trend_CLR$factors),
                                              as.character(yield_trend_CWD$factors),
                                              as.character(yield_trend_BES$factors)
                                        )),
                    type = factor(type, levels = c("Disease leaf incidence alone",
                                      "Coffee variety : CLR leaf incidence",
                                      "Coffee variety : CWD leaf incidence",
                                      "Coffee variety : BES leaf incidence"))) %>%
  ggplot() +
    geom_hline(aes(yintercept = factors), cex =0.2, linetype = 1, color = "gray", alpha =0.3) +
    geom_pointrange(aes(y = factors, x = Slope, xmin = CI_low, xmax = CI_high, colour = type),
                  cex = 0.7, linewidth = 1, position = position_dodge(width = 0.2)) +
    geom_vline(xintercept = 0, cex = 1, linetype = 3, color = "red") +

  #facet_grid(rows = vars(type), scales = "free_y")+
    labs(x= "Estimated slopes for fruit load", y = "Slopes types", col = "Predictors")+
    scale_color_brewer(palette = "Set1") +
    theme_classic()+
    theme(aspect.ratio = 1,
          axis.text.x = element_text(colour = "black", size=13, face="italic", angle = 18, vjust =1, hjust =1),
          axis.text.y = element_text(colour = "black", size=13, face="italic"),
          axis.title = element_text(colour = "black", size=16, face ="bold"),
          panel.border = element_rect(colour = "black", fill = NA, linewidth = 1),
          legend.title = element_text(colour = "black", size=16,
                                      hjust =0.5),
  
          legend.text = element_text(colour = "black", size=13)) -> p_yield_trend_disease

p_yield_trend_disease
```


```{r}
# arrange plot with the package patchwork
p_yield_trend /
p_yield_trend_disease   &
  theme(plot.tag.position  = c(0.2, 1.02),
        plot.tag = element_text(size=16,face="italic"))&
  plot_annotation(tag_levels = 'A') -> yield_trend_plt
yield_trend_plt

```
```{r}
# Function to get significance letter from a contrast dataframe (pairwise comparison dataframe)
get_significance_letters <- function(contrast_df, alpha = 0.05, level_col1 = "Level1", level_col2 = "Level2", p_col = "p") {
  # Extract levels
  all_levels <- unique(c(as.character(contrast_df[[level_col1]]), as.character(contrast_df[[level_col2]])))

  # Initialize an empty matrix of p-values
  pmat <- matrix(NA, nrow = length(all_levels), ncol = length(all_levels),
                 dimnames = list(all_levels, all_levels))

  # Fill in the matrix with provided p-values
  for (i in seq_len(nrow(contrast_df))) {
    l1 <- as.character(contrast_df[[level_col1]][i])
    l2 <- as.character(contrast_df[[level_col2]][i])
    pval <- contrast_df[[p_col]][i]
    pmat[l1, l2] <- pval
    pmat[l2, l1] <- pval
  }
  # Generate letters using multcompView
  comp <- multcompView::multcompLetters(pmat<0.05,compare = "<")$Letters

  # Prepare output dataframe
  output <- data.frame(
    variable = factor(names(comp), levels = all_levels),
    .group = comp,
    stringsAsFactors = FALSE
  )

  return(output)
}
```

```{r}
#### Variety
# Compute estimated mean for each variety
modelbased::estimate_contrasts(mod_yield13,"Coffee_Variety",estimate = "typical", p_adjust = "fdr") -> contrast_variety_df
get_significance_letters(contrast_variety_df) %>%
  mutate(variable = factor(variable , levels = levels(data_yield2$Coffee_Variety))) %>%
  arrange(variable) %>%
  mutate(x= as.numeric(variable))-> compl_letter_yield_var

modelbased::estimate_means(mod_yield13,"Coffee_Variety",estimate = "typical") -> yield_variety

data_yield2 %>%
  ggplot( aes(x = Coffee_Variety, y = berries)) +
  # Add base data
  geom_violin( aes(fill = Coffee_Variety), color = "white", alpha =0.5) +
  scale_fill_viridis(discrete = T)+
  #geom_jitter(width = 0.1, height = 0, alpha = 0.5, size = 3) +
  # Add pointrange and line for means
  geom_text(data = compl_letter_yield_var, aes(x = x, y =2200, label = .group), vjust = 0)+
  geom_pointrange(
    data = yield_variety,
    aes(y = Mean, ymin = CI_low, ymax = CI_high),
    size = 1,
  ) +
   labs(x= "Varieties", y = "Fruit load")+
  theme_classic()+
  theme(aspect.ratio = 1,
        legend.position = "none",
        axis.text.x = element_text(colour = "black", size=13, face="italic", angle = 18, vjust =1, hjust =1),
        axis.text.y = element_text(colour = "black", size=13, face="italic"),
        axis.title = element_text(colour = "black", size=16, face ="bold"),
        panel.border = element_rect(colour = "black", fill = NA, linewidth = 1),
        legend.title = element_text(colour = "black", size=16,
                                    hjust =0.5),

        legend.text = element_text(colour = "black", size=13)) -> p_yield_variety


### Section
# Compute estimated mean for each section
modelbased::estimate_contrasts(mod_yield13, "Section_of_Kaweri",estimate = "typical", p_adjust = "fdr") -> contrast_section_df

get_significance_letters(contrast_section_df) %>%
  mutate(variable = factor(variable , levels = levels(data_yield2$Section_of_Kaweri))) %>%
  arrange(variable) %>%
  mutate(x= as.numeric(variable))-> compl_letter_yield_section

modelbased::estimate_means(mod_yield13,"Section_of_Kaweri",estimate = "typical") -> yield_section

data_yield2 %>%
  ggplot( aes(x = Section_of_Kaweri, y = berries)) +
  # Add base data
  geom_violin(fill= "gray",color = "white") +
  #geom_jitter(width = 0.1, height = 0, alpha = 0.5, size = 3) +
  # Add pointrange and line for means
  geom_text(data = compl_letter_yield_section, aes(x = x, y =1450, label = .group), vjust = 0)+
  geom_pointrange(
    data = yield_section,
    aes(y = Mean, ymin = CI_low, ymax = CI_high),
    size = 1,
  ) +
  theme_minimal()+
   labs(x= "Sections", y = "Yield")+
  theme_classic()+
  theme(aspect.ratio = 1,
        legend.position = "None",
        axis.text.x = element_text(colour = "black", size=13, face="italic", angle = 18, vjust =1, hjust =1),
        axis.text.y = element_text(colour = "black", size=13, face="italic"),
        axis.title = element_text(colour = "black", size=16)) -> p_yield_section




p_yield_variety +
  p_yield_section + theme(axis.title.y = element_blank(), axis.text.y= element_blank())  &
  theme(plot.tag.position  = c(0.2, 1.02),
        plot.tag = element_text(size=16,face="italic"))&
  plot_annotation(tag_levels = 'A')
```

# Figures article

```{r}
p_yield_trend_disease
p_yield_trend
p_yield_variety

ggsave(plot = p_yield_trend_disease, file="results/figures/yield_effect_plot_diseases.pdf",
width=20, height=15,units ="cm")
ggsave(plot = p_yield_trend, file="results/figures/yield_effect_plot_distance.pdf",
width=20, height=15, units ="cm")
ggsave(plot = p_yield_variety, file="results/figures/yield_variety.pdf",
width=20, height=15, units ="cm")


```
# Figures appendix

```{r}

pdf(file ="results/figures/appendix/res_fruit_load.pdf",  
    width = 10,
    height = 6) 

res_yeild <-DHARMa::simulateResiduals(mod_yield13, plot = T)
plot(res_yeild)
dev.off()

pdf(file ="results/figures/appendix/zif_disp_fruit_load.pdf",  
    width = 12,
    height = 4)

par(mfrow = c(1,2))
testZeroInflation(res_yeild)
testDispersion(res_yeild)
dev.off()
```

