---
title: "clean_yield_models"
output: html_document
date: "2025-01-24"
editor_options: 
  chunk_output_type: console
---
# Setup data and packages(no shown)
## 1 Load Packages
```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(ggsci)
library(performance)

library(patchwork)
library(car)
library(glmmTMB)
library(effects)
library(emmeans)
library(ggeffects)
library(DHARMa)

main_theme = theme_minimal()+
  theme(line = element_blank(), 
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        axis.ticks =  element_line(colour = "black"),
        axis.text.x = element_text(colour = "black", size=22, face="italic", angle = 45, vjust = 1, hjust = 1),
        axis.text.y = element_text(colour = "black", size=22, face="italic"),
        legend.title = element_text(colour = "black", size=20,
                                    hjust =0.5),

        legend.text = element_text(colour = "black", size=18),
        axis.title= element_text(size=28),
        strip.text = element_text(colour = "black", size=15, face ="italic"))

convert_dms_to_dd <- function(dms) {
  if(is.na(dms)){
    return(NA)
  }
  if(str_detect(dms, "^\\d+$")){
    return(NA)
  } else{
  dms <- str_replace_all(dms, "[°′″’']", " ") # Replace degree, minute, and second symbols with spaces
  dms_split <- str_split(dms, "\\s+")[[1]]  # Split the string into components
  degrees <- as.numeric(dms_split[1])
  minutes <- as.numeric(dms_split[2])
  seconds <- as.numeric(dms_split[3])
  direction <- dms_split[4]
  
  # Calculate decimal degrees
  decimal_degrees <- degrees + minutes / 60 + seconds / 3600
  if (direction %in% c("S", "W")) {
    decimal_degrees <- -decimal_degrees
  }
  return(decimal_degrees)
  }
}

```

## 2 Arrange data to long format

```{r include=FALSE}
data <- read_xlsx("data/R_PhD_Data_corrected2.xlsx")

data %>% filter(is.na(Shade_tree_Canopy_Cover))
data %>%
  rename(sample_code = "Coffee_soil _sample_CODE") %>%
  # change sample_code names: eg. 
  mutate(sample_code = paste(sample_code,
                             str_extract(Section_of_Kaweri, "^[a-zA-Z]{4}"), sep = "_"),
         Shade_tree_soil_sample_CODE = paste(Shade_tree_soil_sample_CODE,
                             str_extract(Section_of_Kaweri, "^[a-zA-Z]{4}"), sep = "_")) %>%
   mutate(Shade_tree_species = case_when(Shade_tree_species == "Ficus natalensis"~ "Fn",
                                        Shade_tree_species == "Albizia coriaria" ~ "Ac",
                                        Shade_tree_species == "Artocarpus heterophyllus" ~ "Ah",
                                        Shade_tree_species == "Persea americana" ~ "Pa"))-> data



data %>%
  select(Shade_tree_species, Section_of_Kaweri, sample_code, Coffee_Variety,
         Actual_distance_from_shade_tree_m, Shade_tree_Canopy_Cover, Shade_tree_soil_sample_CODE,
         Longitude, Latitude) %>% 
  mutate(Coffee_Variety = case_when(is.na(Coffee_Variety) ~"unknown_var",
                                    .default = Coffee_Variety)) %>%
 
  group_by(Shade_tree_soil_sample_CODE) %>%
  mutate(Shade_tree_Canopy_Cover = mean(Shade_tree_Canopy_Cover, na.rm = T),  ## A little trick to replace NA from Shade_tree_Canopy_Cover to good value
          Longitude = ifelse(is.na(Longitude), first(na.omit(Longitude)), Longitude),
          Latitude = ifelse(is.na(Latitude), first(na.omit(Latitude)), Latitude),
          Longitude_dd = ifelse(!is.na(Longitude), sapply(Longitude, convert_dms_to_dd), NA),
          Latitude_dd = ifelse(!is.na(Latitude), sapply(Latitude, convert_dms_to_dd), NA),
          Coffee_Variety = as.factor(Coffee_Variety),
          Shade_tree_species = as.factor(Shade_tree_species),
          distance_class = cut(
          Actual_distance_from_shade_tree_m,
          breaks = c(0, 8, 16, 24),  # Specify the breakpoints
          labels = c("[0-8]", "(8-16]", "(16-22]"),  # Labels for each range
          right = F) # Indicates whether intervals are right-closed
              ) %>%
  
  ungroup() -> covariate_data
data %>%
  filter(sample_code == "ALB4COF3_Kite") %>% pull(No_CRBD_berries_lower_portion_3rd_branch)
```

Shade tree are correlated to canopy cover
```{r}
covariate_data %>%
  ggplot()+
  geom_boxplot(aes(Shade_tree_species,Shade_tree_Canopy_Cover ))
```

```{r include=FALSE}
### Isolate total cont of leaves or berries per branch
data %>%
  select(sample_code, starts_with("No_berries"),  starts_with("No_leaves")) %>%
  pivot_longer(-sample_code, names_to = "sample_type", values_to = "total_count") %>%
  mutate(
    # Extracting "organ" ("berries" or "leaves")
    organ = str_extract(sample_type, "(?<=_)berries|leaves"),
    
    # Extracting "portion"
    portion = str_extract(sample_type, "(?<=_)lower|Top|middle"),
    
    # Extracting "branch" (e.g., "1st", "2nd", "3rd", "4th")
    branch = str_extract(sample_type, "\\d+(st|nd|rd|th)")
   ) %>%
  select(-sample_type) %>%
  mutate(total_count = case_when(total_count > 250 & organ == "leaves" ~ round(total_count/10),
                            .default = total_count)) %>%  # correct error (5 branch have more than 250 leaves -> error due to one digit added when tipping)
  pivot_wider(names_from = organ, values_from = total_count ) %>%
  group_by(sample_code) %>%
  summarise(berries = sum(berries, na.rm =T),
            leaves = sum(leaves, na.rm =T)) -> total_number_of_leaves_or_berries

### Isolate total count of leaves or berries infected per branchs
data %>%
  select(sample_code, starts_with("No"),  -starts_with("No_berries"),  -starts_with("No_leaves")) %>% # extract colums of total number of leaves/berries and number of leaves/berries infected
  pivot_longer(-sample_code, names_to = "sample_type", values_to = "infected_count") %>%
  mutate(
     # Extracting "disease" (e.g., "CWD", "CLR", "CRBD")
    disease = str_extract(sample_type, "(?<=_)[A-Z]+"),
    
    # Extracting "organ" ("berries" or "leaves")
    organ = str_extract(sample_type, "(?<=_)berries|leaves"),
    
    # Extracting "portion"
    portion = str_extract(sample_type, "(?<=_)lower|Top|middle"),
    
    # Extracting "branch" (e.g., "1st", "2nd", "3rd", "4th")
    branch = str_extract(sample_type, "\\d+(st|nd|rd|th)")
   ) %>%
  select(-sample_type) %>%
  pivot_wider(names_from = c(disease,organ),
              names_glue = "{disease}_infected_{organ}",
              values_from = infected_count  ) %>%
  group_by(sample_code) %>%
  # number of infected leaves and berries per shrubs and disease
  summarise(CWD_infected_leaves = sum(CWD_infected_leaves, na.rm =T),
            CLR_infected_leaves = sum(CLR_infected_leaves, na.rm =T),
            CRBD_infected_leaves = sum(CRBD_infected_leaves, na.rm =T),
            CRBD_infected_berries = sum(CRBD_infected_berries, na.rm =T)) -> number_of_infected_leaves_or_berries


## Merge data and compute severity per branchs
number_of_infected_leaves_or_berries %>%
  left_join(total_number_of_leaves_or_berries, by = join_by("sample_code" == "sample_code")) %>%
  left_join(covariate_data, by = "sample_code") %>%
  mutate(Shade_tree_species = as.factor(Shade_tree_species)) %>%
  rename(distance = "Actual_distance_from_shade_tree_m")%>%
  mutate(berries = as.integer(berries),
         leaves = as.integer(leaves),
         )%>%
  mutate(CWD_severity = CWD_infected_leaves/leaves,
            CLR_severity = CLR_infected_leaves/leaves,
            CRBD_severity = CRBD_infected_leaves/leaves,
            CRBD_severity_berries = CRBD_infected_berries/(berries+1)) -> data_yield

##Remove shrubs with no leaves (dead shrub). Remove all Clone H and D
data_yield %>%
  filter(leaves != 0) %>%
  filter(!(Coffee_Variety %in% c("Clone H", "Clone D"))) %>%
  mutate(Coffee_Variety  = as.factor(as.character(Coffee_Variety)),
         Shade_tree_soil_sample_CODE = as.factor(Shade_tree_soil_sample_CODE),
         Section_of_Kaweri = as.factor(Section_of_Kaweri),
         log_total_count = log(leaves))-> data_yield2

```

# Yield (nbr berries per tree) explain with **severity** 

## Function of residuals check for models

```{r include=FALSE}
# Create a function that take input for a glmm creation. Give em back the model and residuals information.
yield.mod.func2 <- function(data_df, 
                              frml, # Formula for fixed effect of the models
                              fam = gaussian(), # Residuals the models
                              zifrml = "~0", # Formula for zero inflation of the models
                              dispfrml = "~1"){ # Formula for dispersion of the models
  
  # model creation
  mod_yield <-  glmmTMB(formula = formula(frml),
                              family = fam,
                              ziformula = formula(zifrml),
                              dispformula = formula(dispfrml),
                              data = data_df)
  # Compute residuals
  res_yeilds <- DHARMa::simulateResiduals(mod_yield, plot = F)
  # Plot to check the choice of residuals family and the homoscedasticity 
  plot(res_yeilds, quantreg = T)
  
  # Plot to check if dispersion term or zero inflation term is needed
  par(mfrow = c(1, 2))
  testDispersion(res_yeilds)
  testZeroInflation(res_yeilds)
  
  # Plot residuals against some variables
  par(mfrow = c(2, 3))
  plotResiduals(res_yeilds, form = data_df$CRBD_infected_berries, quantreg = T)
  plotResiduals(res_yeilds, form = data_df$distance, quantreg = T)
  plotResiduals(res_yeilds, form = data_df$Shade_tree_species)
  plotResiduals(res_yeilds, form = data_df$Coffee_Variety)
  plotResiduals(res_yeilds, form = data_df$Section_of_Kaweri)
  plotResiduals(res_yeilds, form = data_df$log_total_count)
  par(mfrow = c(2, 2))
  
  # Plot residuals against diseases severities
  plotResiduals(res_yeilds, form = data_df$CRBD_severity_berries, quantreg = T)
  plotResiduals(res_yeilds, form = data_df$CLR_severity, quantreg = T)
  plotResiduals(res_yeilds, form = data_df$CWD_severity, quantreg = T)
  plotResiduals(res_yeilds, form = data_df$CRBD_severity, quantreg = T)
  return(mod_yield)
}
```

## Select a model based on residuals
Try different model, the only constrain is that we keep "distance*Shade_tree_species + (1|Shade_tree_soil_sample_CODE)" .
"distance*Shade_tree_species" : are main effect and interaction in which we are interested 
"Shade_tree_soil_sample_CODE" : mixte effect to correct autocorrelation at the shade tree level. Because number of infected berries per shrubs might be similar around the same individual shade tree due to proximity of shrubs for example.
```{r echo = T, results = 'hide'}
hist(data_yield2$berries %>%log1p)
data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield
data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + Coffee_Variety +
                    (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield2
data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + Coffee_Variety +Section_of_Kaweri +
                    (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield3

data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + distance*Coffee_Variety + Section_of_Kaweri  +
                    (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield4
data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + distance*Coffee_Variety + Section_of_Kaweri  +
                     (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield5

data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + distance*Coffee_Variety + Section_of_Kaweri + 
                    CLR_severity +
                     (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield6
data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + distance*Coffee_Variety + Section_of_Kaweri + 
                    CLR_severity + CRBD_severity + 
                    (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield7
data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + distance*Coffee_Variety + Section_of_Kaweri + 
                    CLR_severity + CRBD_severity + log_total_count +
                    (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield7_bis
data_yield2 %>%
  yield.mod.func2(frml = " berries ~ distance * Shade_tree_species + distance * Coffee_Variety +  
    Section_of_Kaweri + CLR_severity + CRBD_severity + CWD_severity + (1 | Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield8
data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + distance*Coffee_Variety + Section_of_Kaweri + 
                    (CLR_severity + CRBD_severity + CWD_severity)^2 +
                    (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield9
data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + distance*Coffee_Variety + Section_of_Kaweri + 
                    CLR_severity * CRBD_severity * CWD_severity +
                    (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield10
data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + distance*Coffee_Variety + Section_of_Kaweri + 
                    (CLR_severity + CRBD_severity +CWD_severity )*Coffee_Variety+
                    (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield12

data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + distance*Coffee_Variety + Section_of_Kaweri + 
                    (CLR_severity + CRBD_severity )*Coffee_Variety +CWD_severity+
                    (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield13

data_yield2 %>%
  yield.mod.func2(frml = "berries ~ distance*Shade_tree_species + distance*Coffee_Variety + Section_of_Kaweri + 
                    (CLR_severity + CRBD_severity )*Coffee_Variety +CWD_severity+log_total_count +
                    (1|Shade_tree_soil_sample_CODE)",
                    zifrml = "~0",
                    dispfrml = "~ 1",
                    fam = poisson)  -> mod_yield14

```


## Model selection

Select best model (across model with good residuals) based on AIC
```{r}

AIC(mod_yield,mod_yield2, mod_yield3, mod_yield4,mod_yield5,mod_yield6,mod_yield7,mod_yield7_bis,mod_yield8,mod_yield9,mod_yield10,mod_yield13,mod_yield14)


Anova(mod_yield13) %>% round(2)
r2_nakagawa(mod_yield13)
summary(mod_yield13)
```

## Model prediction

### Simple effect

```{r}
predict_response(mod_yield13, c("CLR_severity[all]"), 
                 margin = "empirical",
                 type = "response") %>%
  plot(show_data = T) 

predict_response(mod_yield13, c("CRBD_severity[all]"), 
                 margin = "empirical",
                 type = "response") %>%
  plot(show_data = T) 
predict_response(mod_yield13, c("distance[all]","Coffee_Variety"), 
                 margin = "empirical",
                 type = "response") %>%
  plot(show_data = T) +
  facet_wrap(~group)

predict_response(mod_yield13, c("CLR_severity[all]","Coffee_Variety"), 
                 margin = "empirical",
                 type = "response") %>%
  plot(show_residuals = T) +
  facet_wrap(~group)
predict_response(mod_yield13, c("CRBD_severity[all]","Coffee_Variety"), 
                 margin = "empirical",
                 type = "response") %>%
  plot(show_residuals = T) +
  facet_wrap(~group)
```

### Slope comparison

#### Distance and interaction

```{r}
### Estimate slope values for distance, distance*Shade_tree_species and distance*Coffee_Variety
modelbased::estimate_slopes(mod_yield13,trend = "distance", by = "Shade_tree_species")  %>%
  as.data.frame %>%
  rename(factors = "Shade_tree_species") %>%
  mutate(type = "Shade tree : Distance") -> yield_trend_shade

modelbased::estimate_slopes(mod_yield13, trend = "distance", by = "Coffee_Variety") %>%
  as.data.frame %>%
  rename(factors = "Coffee_Variety") %>%
  mutate(type = "Coffee variety : Distance") -> yield_trend_var

modelbased::estimate_slopes(mod_yield13, trend = "distance") %>%
  as.data.frame %>%
  mutate(type = "Distance alone",
         factors ="Distance") -> yield_trend

### Estimate merge and plot slope values
yield_trend_shade %>%
  bind_rows(yield_trend_var) %>%
  bind_rows(yield_trend) %>%
  mutate(factors = factor(factors, levels = c(as.character(yield_trend_shade$factors),
                                           as.character(yield_trend_var$factors),
                                           as.character(yield_trend$factors))),
         type = factor(type, levels = c("Distance alone",
                                        "Coffee variety : Distance",
                                        "Shade tree : Distance"))) %>%
  ggplot() +
    geom_hline(aes(yintercept = factors), cex =0.2, linetype = 1, color = "gray", alpha =0.5) +
    geom_pointrange(aes(y = factors, x = Slope, xmin = CI_low, xmax = CI_high, colour = type),cex = 0.7, linewidth = 1) +
    geom_vline(xintercept = 0, cex = 1, linetype = 3, color = "red") +
    #facet_grid(rows = vars(type), scales = "free_y")+
    labs(x= "Estimated slope", col = "Slope type")+
    scale_color_d3()+
    theme_classic()+
    theme(aspect.ratio = 1,
          axis.title.y = element_blank(),
          axis.text.x = element_text(colour = "black", size=13, face="italic", angle = 18, vjust =1, hjust =1),
          axis.text.y = element_text(colour = "black", size=13, face="italic"),
          axis.title = element_text(colour = "black", size=16),
          panel.border = element_rect(colour = "black", fill = NA, linewidth = 1),
          legend.title = element_text(colour = "black", size=16,
                                      hjust =0.5),
  
          legend.text = element_text(colour = "black", size=13)) -> p_yield_trend
```


#### Disease and interaction

```{r}
### Estimate slope values for severities and  severities*Coffee_Variety
modelbased::estimate_slopes(mod_yield12, trend = "CLR_severity", by = "Coffee_Variety") %>%
  as.data.frame %>%
  rename(factors = "Coffee_Variety") %>%
  mutate(type = "Coffee variety : CLR severity") -> yield_trend_CLR_var

modelbased::estimate_slopes(mod_yield12, trend = "CRBD_severity", by = "Coffee_Variety") %>%
  as.data.frame %>%
  rename(factors = "Coffee_Variety") %>%
  mutate(type = "Coffee variety : CRBD severity") -> yield_trend_CRBD_var

modelbased::estimate_slopes(mod_yield12, trend = "CLR_severity") %>%
  as.data.frame %>%
  mutate(type = "disease alone",
         factors ="CLR") -> yield_trend_CLR
modelbased::estimate_slopes(mod_yield12, trend = "CWD_severity") %>%
  as.data.frame %>%
  mutate(type = "disease alone",
         factors ="CWD") -> yield_trend_CWD
modelbased::estimate_slopes(mod_yield12, trend = "CRBD_severity") %>%
  as.data.frame %>%
  mutate(type = "disease alone",
         factors ="CRBD") -> yield_trend_CRBD

yield_trend_CLR_var %>%
  bind_rows(yield_trend_CRBD_var) %>%
  bind_rows(yield_trend_CLR) %>%
  bind_rows(yield_trend_CWD) %>%
  bind_rows(yield_trend_CRBD) %>%
  mutate(factors = factor(factors, levels = c(as.character(yield_trend_CLR_var$factors),
                                              as.character(yield_trend_CLR$factors),
                                              as.character(yield_trend_CWD$factors),
                                              as.character(yield_trend_CRBD$factors)
                                        )),
       type = factor(type, levels = c("disease alone",
                                      "Coffee variety : CLR severity",
                                      "Coffee variety : CWD severity",
                                      "Coffee variety : CRBD severity"))) %>%
  filter(Slope<10000) %>%
  ggplot() +
    geom_hline(aes(yintercept = factors), cex =0.2, linetype = 1, color = "gray", alpha =0.5) +
    geom_pointrange(aes(y = factors, x = Slope, xmin = CI_low, xmax = CI_high, colour = type),
                  cex = 0.7, linewidth = 1, position = position_dodge(width = 0.2)) +
    geom_vline(xintercept = 0, cex = 1, linetype = 3, color = "red") +

  #facet_grid(rows = vars(type), scales = "free_y")+
    labs(x= "Estimated slope",y= "Disease alone", col = "Slope type")+
    scale_color_igv()+
    theme_classic()+
    theme(aspect.ratio = 1,
          axis.title.y = element_blank(),
          axis.text.x = element_text(colour = "black", size=13, face="italic", angle = 18, vjust =1, hjust =1),
          axis.text.y = element_text(colour = "black", size=13, face="italic"),
          axis.title = element_text(colour = "black", size=16),
          panel.border = element_rect(colour = "black", fill = NA, linewidth = 1),
          legend.title = element_text(colour = "black", size=16,
                                      hjust =0.5),
  
          legend.text = element_text(colour = "black", size=13)) -> p_yield_trend_disease
p_yield_trend_disease
```


```{r}
p_yield_trend /
p_yield_trend_disease   &
  theme(plot.tag.position  = c(0.2, 1.02),
        plot.tag = element_text(size=16,face="italic"))&
  plot_annotation(tag_levels = 'A') -> yield_trend_plt
yield_trend_plt

```
```{r}
get_significance_letters <- function(contrast_df = contrast_section_df, alpha = 0.05, level_col1 = "Level1", level_col2 = "Level2", p_col = "p") {
  # Extract levels
  all_levels <- unique(c(as.character(contrast_df[[level_col1]]), as.character(contrast_df[[level_col2]])))

  # Initialize an empty matrix of p-values
  pmat <- matrix(NA, nrow = length(all_levels), ncol = length(all_levels),
                 dimnames = list(all_levels, all_levels))

  # Fill in the matrix with provided p-values
  for (i in seq_len(nrow(contrast_df))) {
    l1 <- as.character(contrast_df[[level_col1]][i])
    l2 <- as.character(contrast_df[[level_col2]][i])
    pval <- contrast_df[[p_col]][i]
    pmat[l1, l2] <- pval
    pmat[l2, l1] <- pval
  }
  # Generate letters using multcompView
  comp <- multcompView::multcompLetters(pmat<0.05,compare = "<")$Letters

  # Prepare output dataframe
  output <- data.frame(
    variable = factor(names(comp), levels = all_levels),
    .group = comp,
    stringsAsFactors = FALSE
  )

  return(output)
}
```

```{r}
library(modelbased)
library(RColorBrewer)
library(multcompView)


#### Variety
modelbased::estimate_contrasts(mod_yield13,"Coffee_Variety",estimate = "typical", p_adjust = "fdr") -> contrast_variety_df
get_significance_letters(contrast_variety_df) %>%
  mutate(variable = factor(variable , levels = levels(data_yield2$Coffee_Variety))) %>%
  arrange(variable) %>%
  mutate(x= as.numeric(variable))-> compl_letter_yield_var

modelbased::estimate_means(mod_yield13,"Coffee_Variety",estimate = "typical") -> yield_variety

data_yield2 %>%
  ggplot( aes(x = Coffee_Variety, y = berries)) +
  # Add base data
  geom_violin(aes(fill = Coffee_Variety), color = "white") +
  #geom_jitter(width = 0.1, height = 0, alpha = 0.5, size = 3) +
  # Add pointrange and line for means
  geom_text(data = compl_letter_yield_var, aes(x = x, y =1250, label = .group), vjust = 0)+
  geom_pointrange(
    data = yield_variety,
    aes(y = Mean, ymin = CI_low, ymax = CI_high),
    size = 1,
  ) +
  # Improve colors
  scale_fill_brewer(palette = "Pastel1") +
  scale_color_brewer(palette = "Pastel1") +
  theme_minimal()+
   labs(x= "Varieties", y = "Yield")+
  theme_classic()+
  theme(aspect.ratio = 1,
        legend.position = "None",
        axis.text.x = element_text(colour = "black", size=13, face="italic", angle = 18, vjust =1, hjust =1),
        axis.text.y = element_text(colour = "black", size=13, face="italic"),
        axis.title = element_text(colour = "black", size=16)) -> p_yield_variety


### Section
modelbased::estimate_contrasts(mod_yield13, "Section_of_Kaweri",estimate = "typical", p_adjust = "fdr") -> contrast_section_df

get_significance_letters(contrast_section_df) %>%
  mutate(variable = factor(variable , levels = levels(data_yield2$Section_of_Kaweri))) %>%
  arrange(variable) %>%
  mutate(x= as.numeric(variable))-> compl_letter_yield_section

modelbased::estimate_means(mod_yield13,"Section_of_Kaweri",estimate = "typical") -> yield_section

data_yield2 %>%
  ggplot( aes(x = Section_of_Kaweri, y = berries)) +
  # Add base data
  geom_violin(aes(fill = Section_of_Kaweri), color = "white") +
  #geom_jitter(width = 0.1, height = 0, alpha = 0.5, size = 3) +
  # Add pointrange and line for means
  geom_text(data = compl_letter_yield_section, aes(x = x, y =1450, label = .group), vjust = 0)+
  geom_pointrange(
    data = yield_section,
    aes(y = Mean, ymin = CI_low, ymax = CI_high),
    size = 1,
  ) +
  # Improve colors
  scale_fill_brewer(palette = "Pastel2") +
  scale_color_brewer(palette = "Pastel2") +
  theme_minimal()+
   labs(x= "Sections", y = "Yield")+
  theme_classic()+
  theme(aspect.ratio = 1,
        legend.position = "None",
        axis.text.x = element_text(colour = "black", size=13, face="italic", angle = 18, vjust =1, hjust =1),
        axis.text.y = element_text(colour = "black", size=13, face="italic"),
        axis.title = element_text(colour = "black", size=16)) -> p_yield_section




p_yield_variety +
  p_yield_section + theme(axis.title.y = element_blank(), axis.text.y= element_blank())  &
  theme(plot.tag.position  = c(0.2, 1.02),
        plot.tag = element_text(size=16,face="italic"))&
  plot_annotation(tag_levels = 'A')
```


