---
title: "Shade tree influence on coffee disease"
author: "Mathis Gheno"
date: "2024-12-05"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup-options, include = F}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

# 1 Load Packages




```{r include=FALSE}

# Data manipulation and graphic packages
library(tidyverse)
library(readxl)
library(GGally)
library(viridis)
library(ggsci)
library(patchwork)

# Model and model values extraction packages
library(glmmTMB)
library(DHARMa)
library(car)
library(modelbased)
library(performance)

main_theme = theme_minimal()+
  theme(aspect.ratio = 1,
      axis.line = element_line(colour = "black"),
      panel.border = element_blank(),
      axis.ticks =  element_line(colour = "black"),
      axis.text.x = element_text(colour = "black", size=13, face="italic"),
      axis.text.y = element_text(colour = "black", size=13, face="italic"),
      legend.title = element_text(colour = "black", size=15, hjust =0.5),
      legend.text = element_text(colour = "black", size=13),
      axis.title= element_text(size=16,face="bold"),
      strip.text = element_text(colour = "black", size=15, face ="italic")) 

```

# 2 Arrange data to long format

## 2.1 Compute shrub inscidence of diseases (at tree level)

```{r include=FALSE}
data <- read_xlsx("data/R_PhD_Data_corrected2.xlsx")

data %>%
  rename(sample_code = "Coffee_soil _sample_CODE") %>%
  # change sample names format
  mutate(sample_code = paste(sample_code,
                             str_extract(Section_of_Kaweri, "^[a-zA-Z]{4}"), sep = "_"),
         Shade_tree_soil_sample_CODE = paste(Shade_tree_soil_sample_CODE,
                             str_extract(Section_of_Kaweri, "^[a-zA-Z]{4}"), sep = "_")) %>% 
  mutate(Shade_tree_species = case_when(Shade_tree_species == "Ficus natalensis"~ "Fn",
                                        Shade_tree_species == "Albizia coriaria" ~ "Ac",
                                        Shade_tree_species == "Artocarpus heterophyllus" ~ "Ah",
                                        Shade_tree_species == "Persea americana" ~ "Pa"))-> data


# Isolate covariate from the main dataframe
covariate_data <- data %>%
  dplyr::select(Shade_tree_species, Section_of_Kaweri, sample_code, Coffee_Variety,
         Actual_distance_from_shade_tree_m, Shade_tree_soil_sample_CODE) %>%
  mutate(Coffee_Variety = case_when(Coffee_Variety== "Unidentified" ~"Op2",
                                    Coffee_Variety== "Open pollinated" ~"Op1",
                                    .default = Coffee_Variety))

# Arrange incidence data to a long data frame format and rename variables
 
data %>% 
  # Select occurrence columns 
  dplyr::select(sample_code, starts_with("inc"), starts_with("Inc")) %>%
  pivot_longer(-sample_code, values_to = "value", names_to = "value_type") %>%
  mutate(
    # Extracting "disease" (e.g., "CWD", "CLR", "BES")
    disease = str_extract(value_type, "(?<=_)[A-Z]+"),
    
    # Extracting "portion"
    portion = str_extract(value_type, "(?<=_)lower|Top|middle"),
    
    # Extracting "branch" (e.g., "1st", "2nd", "3rd", "4th")
    branch = str_extract(value_type, "\\d+(st|nd|rd|th)"),
    
    # Extracting "value_type" (e.g., "shrub_incidence" or "shrub_incidence")
    value_type = str_extract(value_type, "^[^_]+"),
    
    # change "Incidence"  to "shrub_incidence")
    value_type = str_replace_all(value_type, "[Ii]ncidence", "shrub_incidence")
  ) %>%
  # some value are above 1,  correct that:
  mutate(value = ifelse(value>=1,1,0 )) %>%
  left_join(covariate_data, by = "sample_code") %>%
  # We have incidence at the branch level (n =12) but we need to incidence at the coffee shrub level. SO we group at sample code that contain the ID of individual coffee shrub and 
  # summarize the covariate at the same time. We do that for each 3 disease.
  group_by(sample_code, disease) %>% 
  summarise(shrub_incidence = ifelse(sum(value, na.rm = T)>=1,1,0), # 0 occurrence = 0 ; 1 to 12 occurrence = 1
            n =  n(),
            distance = unique(Actual_distance_from_shade_tree_m),
            Shade_tree_species = unique(Shade_tree_species),
            Shade_tree_soil_sample_CODE = unique(Shade_tree_soil_sample_CODE),
            Coffee_Variety = unique(Coffee_Variety)) %>%
   ungroup() %>%
   # extract the section name and mutate character column to factor
   mutate(Section_of_kawerie = str_extract(sample_code,"(?<=_).+"),
          across(where(is.character), ~as.factor(.x)))-> data_shrub_incidence

str(data_shrub_incidence)
write.csv(data_shrub_incidence, "outputs/data_shrub_incidence.csv")
```

## 2.2 Compute disease incidence at leaves level for each branch

```{r include=FALSE}
### Isolate total cont of leaves or berries per branch
data %>%
  dplyr::select(sample_code, starts_with("No_berries"),  starts_with("No_leaves")) %>%
  pivot_longer(-sample_code, names_to = "sample_type", values_to = "total_count") %>%
  mutate(
    # Extracting "organ" ("berries" or "leaves")
    organ = str_extract(sample_type, "(?<=_)berries|leaves"),
    
    # Extracting "portion"
    portion = str_extract(sample_type, "(?<=_)lower|Top|middle"),
    
    # Extracting "branch" (e.g., "1st", "2nd", "3rd", "4th")
    branch = str_extract(sample_type, "\\d+(st|nd|rd|th)")
   ) %>%
  dplyr::select(-sample_type) -> total_number_of_leaves_or_berries

### Isolate total count of leaves or berries infected per branchs
data %>%
  dplyr::select(sample_code, starts_with("No"),  -starts_with("No_berries"),  -starts_with("No_leaves")) %>% # extract the total number of leaves/berries and the number of leaves/berries infected
  pivot_longer(-sample_code, names_to = "sample_type", values_to = "infected_count") %>%
  mutate(
     # Extracting "disease" (e.g., "CWD", "CLR", "BES")
    disease = str_extract(sample_type, "(?<=_)[A-Z]+"),
    
    # Extracting "organ" ("berries" or "leaves")
    organ = str_extract(sample_type, "(?<=_)berries|leaves"),
    
    # Extracting "portion"
    portion = str_extract(sample_type, "(?<=_)lower|Top|middle"),
    
    # Extracting "branch" (e.g., "1st", "2nd", "3rd", "4th")
    branch = str_extract(sample_type, "\\d+(st|nd|rd|th)")
   ) -> number_of_infected_leaves_or_berries

## Merge data and compute serverity per branchs
number_of_infected_leaves_or_berries %>%
  left_join(total_number_of_leaves_or_berries, by = join_by("sample_code" == "sample_code",
                                                            "branch" == "branch",
                                                            "portion" == "portion",
                                                            "organ" == "organ")) %>%
  mutate(leaf_incidence = infected_count/total_count) %>%
  left_join(covariate_data, by = "sample_code") %>%
  mutate(Shade_tree_species = as.factor(Shade_tree_species)) %>%
  rename(distance = "Actual_distance_from_shade_tree_m") %>%
  mutate(distance_class = cut(
      distance,
      breaks = c(0, 8, 16, 24),  # Specify the breakpoints for distance class
      labels = c("[0-8]", "(8-16]", "(16-22]"),  # Labels for each range
      right = F), # Indicates whether intervals are right-closed
    total_count = case_when(total_count > 250 ~ round(total_count/10), # correct error (5 branch have more than 250 leaves -> error due to one digit added when tipping)
                            .default = total_count),
    log_total_count = log(total_count),
    across(where(is.character),~as.factor(.x))) -> data_leaf_incidence

write.csv(data_leaf_incidence, "outputs/data_leaf_incidence.csv")
```


```{r include=FALSE}
data_leaf_incidence %>%
  filter(disease == "CWD") %>%
  select(sample_code) %>%
  distinct(sample_code) %>%
  mutate(shade_tree = str_extract(sample_code,"(^[A-Za-z]+)(\\d+)(.{4})_(.{4})", group = 1),
         coffe_shrub = str_extract(sample_code,"(^[A-Za-z]+\\d+)(.{4})_(.{4})", group = 2),
         section = str_extract(sample_code,"(^[A-Za-z]+\\d+)(.{4})_(.{4})", group = 3)) -> temp

table(temp$section)

temp %>%
  filter(section=="Kita") %>%
  pull(shade_tree) %>%
  table()/3

temp %>%
  filter(section=="Kite") %>%
  pull(shade_tree) %>%
  table()/3

temp %>%
  filter(section=="Kyam") %>%
  pull(shade_tree) %>%
  table()/3

temp %>%
  filter(section=="Luwu") %>%
  pull(shade_tree) %>%
  table()/3

temp %>%
  filter(section=="Nonv") %>%
  pull(shade_tree) %>%
  table()/3

temp %>%
  pull(shade_tree) %>%
  table()/3
```



## 2.3 Data cleaning

### 2.3.1 Tree with no leaves (to remove)

```{r include=FALSE}

data_leaf_incidence%>%
  group_by(sample_code)%>%
  summarise(total_count = sum(total_count, na.rm = T)) %>%
  filter(total_count ==0) %>%
  pull(sample_code)-> no_leave_trees
```

before removing tree with no leaves

```{r}
data_shrub_incidence %>%
  group_by(Shade_tree_species, disease) %>%
  mutate(n_tot = n(),
            infected_count = sum(shrub_incidence,na.rm  =T)) %>%
  ggplot()+
  facet_wrap(~disease) +
  geom_bar(aes(Shade_tree_species, fill = as.factor(shrub_incidence)), position = "fill") +
  geom_text(aes(x=Shade_tree_species, y=0.2,group = Shade_tree_species, label = infected_count), col = "white") +
  geom_text(aes(x=Shade_tree_species, y=1.04,group = Shade_tree_species, label = n_tot)) +
  scale_fill_startrek() +
  labs(x = " Shade tree", y = "Proportion", fill = "Whole shrub\n incidence") +
  main_theme +
    theme(
        axis.text.x = element_text(colour = "black", size=14, face="italic", angle = 45, vjust = 1, hjust = 1))

data_shrub_incidence %>%
  group_by(Shade_tree_species, Coffee_Variety,disease) %>%
  mutate(n_tot = n(),
            infected_count = sum(shrub_incidence,na.rm  =T)) %>%
  ggplot()+
  facet_wrap(~Coffee_Variety*disease) +
  geom_bar(aes(Shade_tree_species, fill = as.factor(shrub_incidence)), position = "fill") +
  geom_text(aes(x=Shade_tree_species, y=0.2,group = Shade_tree_species, label = infected_count), col = "white") +
  geom_text(aes(x=Shade_tree_species, y=1.04,group = Shade_tree_species, label = n_tot)) +
  scale_fill_startrek() +
  labs(x = " Shade tree", y = "Proportion", fill = "Whole shrub\n incidence") +
  main_theme
```

after removing tree with no leaves
```{r}
data_shrub_incidence %>%
  filter(!(sample_code %in% no_leave_trees)) -> data_shrub_incidence

data_shrub_incidence %>%
  group_by(Shade_tree_species, disease) %>%
  mutate(n_tot = n(),
            infected_count = sum(shrub_incidence,na.rm  =T)) %>%
  ggplot()+
  facet_wrap(~disease) +
  geom_bar(aes(Shade_tree_species, fill = as.factor(shrub_incidence)), position = "fill") +
  geom_text(aes(x=Shade_tree_species, y=0.2,group = Shade_tree_species, label = infected_count), col = "white") +
  geom_text(aes(x=Shade_tree_species, y=1.04,group = Shade_tree_species, label = n_tot)) +
  scale_fill_startrek() +
  labs(x = " Shade tree", y = "Proportion", fill = "Whole shrub\n incidence") +
  main_theme +
    theme(
        axis.text.x = element_text(colour = "black", size=14, face="italic", angle = 45, vjust = 1, hjust = 1))
data_shrub_incidence %>%
  group_by(Shade_tree_species, Coffee_Variety,disease) %>%
  mutate(n_tot = n(),
            infected_count = sum(shrub_incidence,na.rm  =T)) %>%
  ggplot()+
  facet_wrap(~Coffee_Variety*disease) +
  geom_bar(aes(Shade_tree_species, fill = as.factor(shrub_incidence)), position = "fill") +
  geom_text(aes(x=Shade_tree_species, y=0.2,group = Shade_tree_species, label = infected_count), col = "white") +
  geom_text(aes(x=Shade_tree_species, y=1.04,group = Shade_tree_species, label = n_tot)) +
  scale_fill_startrek() +
  labs(x = " Shade tree", y = "Proportion", fill = "Whole shrub\n incidence") +
  main_theme
```

### 2.3.2 Under represented clones (to remove)

before removing clone H and D

```{r}
data_shrub_incidence %>%
  filter( disease == "CWD") %>%
  group_by(Shade_tree_species, Coffee_Variety) %>%
  mutate(n_tot = n(),
            infected_count = sum(shrub_incidence,na.rm  =T)) %>%
  ggplot()+
  facet_wrap(~Coffee_Variety) +
  geom_bar(aes(Shade_tree_species, fill = as.factor(shrub_incidence)), position = "fill") +
  geom_text(aes(x=Shade_tree_species, y=0.2,group = Shade_tree_species, label = infected_count), col = "white") +
  geom_text(aes(x=Shade_tree_species, y=1.04,group = Shade_tree_species, label = n_tot)) +
  scale_fill_startrek() +
  labs(x = " Shade tree", y = "Proportion", fill = "shrub_incidence") +
  main_theme
```

after removing clone H and D

```{r}
 data_shrub_incidence %>%
  filter(!(Coffee_Variety %in% c("Clone H", "Clone D"))) %>%
   mutate(Coffee_Variety  = as.factor(as.character(Coffee_Variety))) -> data_shrub_incidence
data_shrub_incidence %>%
  filter( disease == "CWD") %>%
  group_by(Shade_tree_species, Coffee_Variety) %>%
  mutate(n_tot = n(),
            infected_count = sum(shrub_incidence,na.rm  =T)) %>%
  ggplot()+
  facet_wrap(~Coffee_Variety) +
  geom_bar(aes(Shade_tree_species, fill = as.factor(shrub_incidence)), position = "fill") +
  geom_text(aes(x=Shade_tree_species, y=0.2,group = Shade_tree_species, label = infected_count), col = "white") +
  geom_text(aes(x=Shade_tree_species, y=1.04,group = Shade_tree_species, label = n_tot)) +
  scale_fill_startrek() +
  labs(x = " Shade tree", y = "Proportion", fill = "Whole shrub\n incidence") +
  main_theme
```
```{r}
 data_shrub_incidence %>%
  filter(!(Coffee_Variety %in% c("Clone H", "Clone D"))) %>%
   mutate(Coffee_Variety  = as.factor(as.character(Coffee_Variety))) -> data_shrub_incidence
data_shrub_incidence %>%
  filter( disease == "CWD") %>%
  group_by(Shade_tree_species, Coffee_Variety) %>%
  mutate(n_tot = n(),
            infected_count = sum(shrub_incidence,na.rm  =T)) %>%
  ggplot()+
  facet_wrap(~Coffee_Variety) +
  geom_bar(aes(Shade_tree_species))+
  geom_text(aes(x=Shade_tree_species, y=1.5,group = Shade_tree_species, label = n_tot)) +

  labs(x = " Shade tree", y = "n replicats of the combinaison") +
  main_theme
```

```{r}
data_shrub_incidence %>%
  filter(!(Coffee_Variety %in% c("Clone H", "Clone D"))) %>%
   mutate(Coffee_Variety  = as.factor(as.character(Coffee_Variety))) -> data_shrub_incidence
data_shrub_incidence %>%
  filter( disease == "CWD") %>%
  group_by(Section_of_kawerie, Coffee_Variety) %>%
  mutate(n_tot = n(),
            infected_count = sum(shrub_incidence,na.rm  =T)) %>%
  ggplot()+
  facet_wrap(~Coffee_Variety) +
  geom_bar(aes(Section_of_kawerie))+
  geom_text(aes(x=Section_of_kawerie, y=1.5,group = Section_of_kawerie, label = n_tot)) +

  labs(x = " Shade Section_of_kawerie", y = "n replicats of the combinaison") +
  main_theme
```


```{r include=FALSE}
data_leaf_incidence %>%
  filter(!(sample_code %in% no_leave_trees))%>%
  filter(!(Coffee_Variety %in% c("Clone H", "Clone D"))) %>%
   mutate(Coffee_Variety  = as.factor(as.character(Coffee_Variety))) -> data_leaf_incidence
```



# 3 Whole shrub incidence model

```{r}
# Create a function that take input for a glm creation. Give back the model and residuals informations.
shrub_incidence.mod.func <- function(data, 
                              frml){ # Formula for fixed effect of the models
  # Compute the model
  mod_leaf_incidence <-  glmmTMB(formula = formula(frml),
                              family = binomial(),# shrub_incidence is 1 or 0 (win or lose trial) => binomial family
                              data = data)
  # Compute residuals
  res_leaf_incidence <- DHARMa::simulateResiduals(mod_leaf_incidence, plot = TRUE)


  par(mfrow = c(2, 3))
  
  # Plot to check if dispersion term or zero inflation term is needed
  testDispersion(res_leaf_incidence)
  testZeroInflation(res_leaf_incidence)
  
  # Plot residuals against some variables of interest
  plotResiduals(res_leaf_incidence, form = data$distance )
  plotResiduals(res_leaf_incidence, form = data$Shade_tree_species)
  plotResiduals(res_leaf_incidence, form = data$Section_of_kawerie)
  plotResiduals(res_leaf_incidence, form = data$Coffee_Variety)
  par(mfrow = c(1, 1))
  
  return(mod_leaf_incidence)
}
```
## 3.1 CWD whole shrub incidence data

### Compute models

```{r}
data_shrub_incidence %>%
  filter(disease == "CWD") %>% 
  droplevels() -> binary_data_CWD
```

```{r}
full_berrie_model <-  glmmTMB(formula = shrub_incidence ~ Shade_tree_species * distance * Coffee_Variety   + (1|Section_of_kawerie/Shade_tree_soil_sample_CODE),
                            family = binomial(),
                            data = binary_data_CWD,
                    na.action = "na.fail")

MuMIn::dredge(global.model = full_berrie_model,
                fixed = c("cond(distance)", "cond(Shade_tree_species)",
                          "cond(distance:Shade_tree_species)",
                          "cond(Section_of_kawerie)")) -> dd_shrub_incidence
length(dd_shrub_incidence[[1]])
dim(dd_shrub_incidence)
subset(dd_shrub_incidence, delta < 4)
plot(dd_shrub_incidence)
data.frame(dd_shrub_incidence)
```

```{r}
for(i in 1:5){
  binary_data_CWD %>%
    shrub_incidence.mod.func(frml = formula(MuMIn::get.models(dd_shrub_incidence, i)[[1]])
    )
  } 
```

```{r}
MuMIn::get.models(dd_shrub_incidence, 1)[[1]] -> selected_model_shrub_incidence
```

```{r}
## Anova 
car::Anova(selected_model_shrub_incidence, 2) %>%
  round(2)

performance::r2_nakagawa(selected_model_shrub_incidence)
```

### Plot results

```{r}
# Function to get significance letter from a contrast dataframe (pairwise comparison dataframe)
get_significance_letters2 <- function(contrast_df, alpha = 0.05, level_col1 = "Level1", level_col2 = "Level2") {
  # Extract levels
  
  split_contrast <- contrast_df$contrast %>% str_split(" - ",simplify = TRUE)
  l1 <- split_contrast[,1]
  l2 <- split_contrast[,2]
  
  all_levels <- unique(c(l1, l2))
  # Initialize an empty matrix of p-values
  pmat <- matrix(NA, nrow = length(all_levels), ncol = length(all_levels),
                 dimnames = list(all_levels, all_levels))

  # Fill in the matrix with provided p-values

  for (i in seq_len(nrow(contrast_df))) {
    pval <- contrast_df$p.value[i]
    pmat[l1[i], l2[i]] <- pval
    pmat[l2[i], l1[i]] <- pval
  }
  # Generate letters using multcompView
  comp <- multcompView::multcompLetters(pmat<0.05,compare = "<")$Letters

  # Prepare output dataframe
  output <- data.frame(
    variable = factor(names(comp), levels = all_levels),
    .group = comp,
    stringsAsFactors = FALSE
  )

  return(output)
}
```

```{r}
# Function to get significance letters from a `hypotheses()` output (e.g. after
# applying a multiple-comparison correction with `multcomp = "BH"`).
# That object no longer carries a `contrast` column ("Clone B - Clone A", ...)
# directly: the labels have to be recovered from the nested `comparisons`
# object stored in its `marginaleffects` attribute (`@model$contrast`), which
# keeps the same row order as `hyp_df` since `hypotheses()` only recomputes
# the p-values/CIs in place and does not reorder or aggregate rows.
get_significance_letters3 <- function(hyp_df, alpha = 0.05) {
  # Recover the "Level1 - Level2" contrast labels
  if ("contrast" %in% names(hyp_df)) {
    contrast_labels <- hyp_df$contrast
  } else {
    contrast_labels <- attr(hyp_df, "marginaleffects")@model$contrast
  }

  if (is.null(contrast_labels) || length(contrast_labels) != nrow(hyp_df)) {
    stop("Could not recover contrast labels matching the number of rows of `hyp_df`.")
  }

  # Extract levels
  split_contrast <- contrast_labels %>% str_split(" - ", simplify = TRUE)
  l1 <- split_contrast[,1]
  l2 <- split_contrast[,2]

  all_levels <- unique(c(l1, l2))
  # Initialize an empty matrix of (already corrected) p-values
  pmat <- matrix(NA, nrow = length(all_levels), ncol = length(all_levels),
                 dimnames = list(all_levels, all_levels))

  # Fill in the matrix with the corrected p-values
  for (i in seq_len(nrow(hyp_df))) {
    pval <- hyp_df$p.value[i]
    pmat[l1[i], l2[i]] <- pval
    pmat[l2[i], l1[i]] <- pval
  }
  # Generate letters using multcompView
  comp <- multcompView::multcompLetters(pmat < alpha, compare = "<")$Letters

  # Prepare output dataframe
  output <- data.frame(
    variable = factor(names(comp), levels = all_levels),
    .group = comp,
    stringsAsFactors = FALSE
  )

  return(output)
}
```



```{r}
marginaleffects::datagrid(model = selected_model_shrub_incidence, Coffee_Variety =c("Clone A", "Clone B", "Clone C", "Clone F", "Op1", "Op2") , grid_type = "counterfactual") -> datgrid_shrub_incidence1

marginaleffects::avg_predictions(
  selected_model_shrub_incidence,
  by = "Coffee_Variety",
  newdata = datgrid_shrub_incidence1,
) -> shrub_incidence_variety

marginaleffects::avg_comparisons(
  selected_model_shrub_incidence,
  variables = list(Coffee_Variety = "pairwise")
) %>%
  marginaleffects::hypotheses(multcomp = "BH") -> contrast_shrub_incidence_variety_df

# estimate_relation(mod_leaf_incidence_BES_leaves_top6, by = c("Coffee_Variety") ) -> BES_leaf_incidence_variety
#
# estimate_contrasts(BES_leaf_incidence_variety, contrast = c("Coffee_Variety"), p_adjust = "fdr") -> contrast_BES_leaf_incidence_variety_df
# str(contrast_BES_leaf_incidence_variety_df)
# contrast_BES_leaf_incidence_variety_df %>% str

get_significance_letters3(contrast_shrub_incidence_variety_df) %>%
  mutate(variable = factor(variable , levels = levels(data_shrub_incidence$Coffee_Variety))) %>%
  arrange(variable) %>%
  mutate(x= as.numeric(variable))-> compl_letter_shrub_incidence_var

shrub_incidence_variety %>%
  ggplot() +
    geom_pointrange(
    aes(x= Coffee_Variety , y = estimate , ymin = conf.low, ymax = conf.high),
    size = 0.75,linewidth = 1
  ) +
  geom_text(data = compl_letter_shrub_incidence_var, aes(x = x, y =0.95, label = .group), vjust = 0) +
  scale_y_continuous(limits = c(0,1)) +
  labs(x= "Coffee variety", y = "CWD shrub incidence probability") +
  theme_classic() +
  theme(aspect.ratio = 1,
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        axis.ticks =  element_line(colour = "black"),
        axis.text.x = element_text(colour = "black", size=13, face="italic", angle = 25, vjust = 1, hjust =1),
        axis.text.y = element_text(colour = "black", size=13, face="italic"),
        legend.text = element_text(colour = "black", size=18),
        axis.title= element_text(size=16,face="bold"),
        strip.text = element_text(colour = "black", size=15, face ="italic")) -> p1_shrub_incidence

shrub_incidence_variety %>%
  data.frame
contrast_shrub_incidence_variety_df %>%
  data.frame
p1_shrub_incidence
```





```{r}
marginaleffects::datagrid(model = selected_model_shrub_incidence, distance= c(0,5,10,15,20), Shade_tree_species = c("Fn", "Ah", "Pa", "Ac"), grid_type = "counterfactual") -> datgrid_shrub_incidence2

marginaleffects::avg_predictions(selected_model_shrub_incidence, by = c("distance", "Shade_tree_species"), newdata = datgrid_shrub_incidence2) %>% 
  as.data.frame() %>%
  ggplot()+
  geom_ribbon(aes(distance,estimate, ymin= conf.low, ymax = conf.high, fill = Shade_tree_species), alpha = 0.3, linewidth = 1) +
  geom_line(aes(x=distance,estimate, col = Shade_tree_species), linewidth = 1) +
  geom_point(data = binary_data_CWD, aes(distance,shrub_incidence, fill = Shade_tree_species),
             alpha = 0.8, shape = 21, cex = 3, color="black",show.legend = F)+
  facet_grid(row = vars(Shade_tree_species), switch="both")+
  scale_y_continuous(limits = c(0,1))+
  labs(x = "Distance from\n shade tree (m)", y = "CWD shrub incidence probability") +
  scale_fill_viridis(option = "viridis",discrete = T )+
  scale_color_viridis(option = "viridis",discrete = T )+
  theme_classic()+
  theme(aspect.ratio = 1,
        plot.margin = margin(0, 0, 0, 0),
        axis.title.x = element_blank(),
        legend.position = "None",
        panel.border = element_rect(colour = "black", fill = NA, linewidth = 1),
        axis.title.y = element_text(colour = "black", size=14, face="italic")) -> p2_shrub_incidence
p2_shrub_incidence

#Slope pairwise comparison shade tree
marginaleffects::avg_slopes(selected_model_shrub_incidence,
                            variables = "distance",
                            by= "Shade_tree_species",
                            newdata  = datgrid_shrub_incidence2) %>%
data.frame()

```


```{r}
layout2 <- c(
  patchwork::area(t = 0, l = 0, b =10, r = 3.5),
  patchwork::area(t = 0, l = 2, b = 10, r = 10)
)
p2_shrub_incidence+theme(axis.title.x =  element_text(size=16,face="bold"),
         axis.title.y =  element_text(size=16,face="bold"))+
  p1_shrub_incidence+theme(axis.title.y = element_blank())+
  patchwork::plot_layout(design = layout2) &
  theme(plot.tag.position  = c(0.25, 1),
        plot.tag = element_text(size=16,face="italic"))&
  plot_annotation(tag_levels = 'A') -> plot_cwd_shrub_incidence


plot_cwd_shrub_incidence
```


## 3.2 Recap shrub incidence

```{r}
data_shrub_incidence %>%
 mutate(disease = case_when(disease == "BES" ~ "BES",
                             .default = disease)) %>%
  mutate(Shade_tree_species) %>%
  group_by(Shade_tree_species, disease) %>%
  mutate(n_tot = n(),
            infected_count = sum(shrub_incidence,na.rm  =T)) %>%
   mutate(shrub_incidence = case_when(shrub_incidence == 1 ~ "Present",
                                    shrub_incidence == 0 ~ "Absent")) %>%
  ggplot()+
  facet_wrap(~disease) +
  geom_bar(aes(Shade_tree_species, fill = as.factor(shrub_incidence)), position = "fill") +
  geom_text(aes(x=Shade_tree_species, y=0.2,group = Shade_tree_species, label = infected_count), col = "white") +
  geom_text(aes(x=Shade_tree_species, y=1.04,group = Shade_tree_species, label = n_tot)) +
  scale_fill_viridis(discrete = T) +
  labs(x = " Shade tree species", y = "Proportion of coffee shrubs", fill = "Disease incidence\n at shrubs level") +
  theme_minimal()+
  theme(aspect.ratio = 1,
      axis.line = element_line(colour = "black"),
      panel.border = element_blank(),
      axis.ticks =  element_line(colour = "black"),
      axis.text.x = element_text(colour = "black", size=13, face="italic"),
      axis.text.y = element_text(colour = "black", size=13, face="italic"),
      legend.title = element_text(colour = "black", size=15, hjust =0.5),
      legend.text = element_text(colour = "black", size=13),
      axis.title= element_text(size=16,face="bold"),
      strip.text = element_text(colour = "black", size=15, face ="italic")) -> disease_shrub_incidence

disease_shrub_incidence
```

# 4 Leaf incidence model

## 4.1 Leaf incidence correlation between diseases

```{r echo=FALSE}
data_leaf_incidence %>%
  # remove berries data (not used)
  filter(organ != "berries") %>% 
  mutate(disease = case_when(disease == "CRBD" ~ "BES", # BES on leaves = BES vs BES on berries = BES. So here we are just looking at BES becasue we only analise leaves
                           .default = disease)) %>%
  mutate(portion = case_when(portion == "lower" ~"Lower",
                             portion == "middle"~"Middle",
                             portion == "Top"~"Upper"),
         portion = factor(portion, levels = c("Upper","Middle","Lower"))) %>%
  dplyr::select(leaf_incidence, sample_code, disease,branch,portion) %>%
  pivot_wider(names_from = disease, values_from = leaf_incidence) %>% 
  dplyr::select(CWD, CLR, BES, portion) %>%
  ggpairs(columns = 1:3,
          mapping = ggplot2::aes(color = portion,
                                
                                 alpha =1),
          diag = list(continuous = wrap("barDiag", alpha=1 )),
          upper = list(continuous = wrap("cor", size = 5, alpha =1))) +
  labs(x = "Incidence proportion per branch", y = "Incidence proportion per branch (scatterplot)\n or branch count(barplot)")+
  # scale_color_lancet()+
  # scale_fill_lancet()+
  viridis::scale_fill_viridis( discrete = T) +
  viridis::scale_color_viridis( discrete = T) +
  theme_classic() +
  theme (axis.line = element_line(colour = "black"),
        axis.ticks =  element_line(colour = "black"),
        legend.text = element_text(colour = "black", size=18),
        axis.title= element_text(size=16,face="bold"),
        strip.text = element_text(colour = "black", size=15, face ="italic"),
        panel.border = element_rect(colour = "black", fill = NA, linewidth = 1)) -> disease_correlation_plot
disease_correlation_plot
```


### 4.2 Leaf incidence model and residual function

```{r include=FALSE}

leaf_incidence.mod.func <- function(data, 
                              frml,
                              zifrml,
                              disprml = formula("~1")){
  # Compute model
  mod_leaf_incidence <-  glmmTMB(formula = frml,
                              ziformula = zifrml,
                              dispformula = disprml,
                              family = beta_family(),
                              data = data)
  
  # Compute residuals
  res_leaf_incidence <- DHARMa::simulateResiduals(mod_leaf_incidence, plot = TRUE)


  par(mfrow = c(2, 3))
  
  # Test dispersion nand zero inflation
  testDispersion(res_leaf_incidence)
  testZeroInflation(res_leaf_incidence)
  
  # Plot residuals against some variables of interest
  plotResiduals(res_leaf_incidence, form = data$distance)
  plotResiduals(res_leaf_incidence, form = data$Shade_tree_species)
  plotResiduals(res_leaf_incidence, form = data$log_total_count)
  plotResiduals(res_leaf_incidence, form = data$Coffee_Variety)
  par(mfrow = c(1, 1))
  
  return(mod_leaf_incidence)
}

```

```{r include=FALSE}
data_leaf_incidence %>%
  ggplot() +
  facet_wrap(~disease) +
  geom_point(aes(x = log_total_count, y = leaf_incidence)) +
  labs(x = "Log(Total leaf count)", y = "Diseases incidence proportion per branch") +
  main_theme
```

## 4.3 BES Leaf incidence model

```{r include=FALSE}
data_leaf_incidence %>%
  filter(disease == "CRBD", organ =="leaves") %>%
  filter(!(Coffee_Variety %in% c("Clone H", "Clone D"))) %>%
  mutate(Coffee_Variety = as.factor(as.character(Coffee_Variety))) -> data_leaf_incidence_BES_leaves
```




### Compute models

Select only top portion of the shrub and change leaf incidence of 1 to 0.999 to respect range of beta distribution

```{r include=FALSE}
data_leaf_incidence_BES_leaves %>%
  filter(portion =="Top", !is.na(leaf_incidence)) %>%
  mutate(leaf_incidence = case_when(leaf_incidence == 1 ~ 0.999,
                                    .default = leaf_incidence))  -> BES_leaves_top
```


### Model selection

```{r}
full_model_BES_branch_incidence <-  glmmTMB(formula = leaf_incidence ~ Shade_tree_species * distance * Coffee_Variety  + (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/sample_code),
                            ziformula = ~ 1,
                            family = beta_family(),
                            data = BES_leaves_top,
                    na.action = "na.fail")

MuMIn::dredge(global.model = full_model_BES_branch_incidence,
                fixed = c("cond(distance)", "cond(Shade_tree_species)",
                          "cond(distance:Shade_tree_species)")) -> dd_BES_branch_incidence
length(dd_BES_branch_incidence[[1]])
```

```{r}
for(i in 1:5){
  BES_leaves_top %>%
    leaf_incidence.mod.func(frml = formula(MuMIn::get.models(dd_BES_branch_incidence, i)[[1]]),
                            zifrml = formula("~1"),
                            disprml = formula("~1")
                            
    )
  } 
```

```{r}
full_model_BES_branch_incidence_disp <-  glmmTMB(formula = leaf_incidence ~ Shade_tree_species * distance * Coffee_Variety   + (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/sample_code),
                            ziformula = ~ 1,
                            dispformula = ~ log_total_count,
                            family = beta_family(),
                            data = BES_leaves_top,
                    na.action = "na.fail")

MuMIn::dredge(global.model = full_model_BES_branch_incidence_disp,
                fixed =  c("cond(distance)", "cond(Shade_tree_species)",
                          "cond(distance:Shade_tree_species)")) -> dd_BES_branch_incidence_disp

length(dd_BES_branch_incidence_disp[[1]])
subset(dd_BES_branch_incidence_disp, delta < 2)
```

```{r}
for(i in 1:5){
 
  BES_leaves_top %>%
    leaf_incidence.mod.func(frml = formula(MuMIn::get.models(dd_BES_branch_incidence_disp, i)[[1]]),
                            zifrml = formula("~1"),
                            disprml = formula("~log_total_count")
                            
    )
  print(formula(MuMIn::get.models(dd_BES_branch_incidence_disp, i)[[1]]))
  } 
```

```{r}
full_model_BES_branch_incidence_disp_zif <-  glmmTMB(formula = leaf_incidence ~ Shade_tree_species * distance * Coffee_Variety  +  (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/sample_code),
                            ziformula = ~ Coffee_Variety,
                            dispformula = ~ log_total_count,
                            family = beta_family(),
                            data = BES_leaves_top,
                    na.action = "na.fail")

MuMIn::dredge(global.model = full_model_BES_branch_incidence_disp_zif,
                fixed =  c("cond(distance)", "cond(Shade_tree_species)",
                          "cond(distance:Shade_tree_species)","cond(Section_of_Kaweri)")) -> dd_BES_branch_incidence_disp_zif

length(dd_BES_branch_incidence_disp_zif[[1]])
subset(dd_BES_branch_incidence_disp_zif, delta < 2)
length(dd_BES_branch_incidence_disp_zif)

```

```{r}
for(i in 1:5){
 
  BES_leaves_top %>%
    leaf_incidence.mod.func(frml = formula(MuMIn::get.models(dd_BES_branch_incidence_disp_zif, i)[[1]]),
                            zifrml = formula("~Coffee_Variety"),
                            disprml = formula("~log_total_count")
                            
    )
  print(formula(MuMIn::get.models(dd_BES_branch_incidence_disp_zif, i)[[1]]))
  } 
```

```{r}
MuMIn::get.models(dd_BES_branch_incidence_disp_zif, 1)[[1]] -> selected_model_shrub_incidence_BES
```


### Model estimation

```{r}
# Anova
car::Anova(selected_model_shrub_incidence_BES) %>%
  round(2)
car::Anova(selected_model_shrub_incidence_BES, component = "zi") 

car::Anova(selected_model_shrub_incidence_BES, component = "disp")

# performance::r2_nakagawa(mod_leaf_incidence_BES_leaves_top6)
#             null_model =   glmmTMB(formula = leaf_incidence~1,
#                               ziformula = ~1,
#                               dispformula = ~1,
#                               family = beta_family(),
#                               #weights = total_count ,
#                               data = BES_leaves_top),
#             model_component ="full")
```


```{r}
marginaleffects::datagrid(model = selected_model_shrub_incidence_BES, Coffee_Variety =c("Clone A", "Clone B", "Clone C", "Clone F", "Op1", "Op2") , grid_type = "counterfactual") -> datagrid_leaf_incidence_BES

marginaleffects::avg_predictions(
  selected_model_shrub_incidence_BES,
  by = "Coffee_Variety",
  type = "response",
  newdata = datagrid_leaf_incidence_BES
) -> BES_leaf_incidence_variety 

marginaleffects::avg_comparisons(
  selected_model_shrub_incidence_BES,
  type= "response",
  variables = list(Coffee_Variety = "pairwise")
) %>%
  marginaleffects::hypotheses(multcomp = "BH") -> contrast_BES_leaf_incidence_variety_df

# estimate_relation(mod_leaf_incidence_BES_leaves_top6, by = c("Coffee_Variety") ) -> BES_leaf_incidence_variety
#
# estimate_contrasts(BES_leaf_incidence_variety, contrast = c("Coffee_Variety"), p_adjust = "fdr") -> contrast_BES_leaf_incidence_variety_df
# str(contrast_BES_leaf_incidence_variety_df)
# contrast_BES_leaf_incidence_variety_df %>% str

get_significance_letters3(contrast_BES_leaf_incidence_variety_df) %>%
  mutate(variable = factor(variable , levels = levels(BES_leaves_top$Coffee_Variety))) %>%
  arrange(variable) %>%
  mutate(x= as.numeric(variable))-> compl_letter_BES_leaf_incidence_var



ggplot(BES_leaf_incidence_variety, aes(x = Coffee_Variety, y = estimate)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), linewidth = 1) +
   geom_text(data = compl_letter_BES_leaf_incidence_var, aes(x = x, y =0.20, label = .group), vjust = 0)+
  labs(x= "Variety", y = "BES incidence proportion per branch")+
  theme_classic()+
  theme(aspect.ratio = 1,
        axis.text.x = element_text(colour = "black", size=13, face="italic", angle = 18, vjust =1, hjust =1),
        axis.text.y = element_text(colour = "black", size=13, face="italic"),
        axis.title = element_text(colour = "black", size=16)) -> p_BES_leaf_incidence_variety

p_BES_leaf_incidence_variety
```

## 4.4 CWD leaf incidence model

```{r include=FALSE}
data_leaf_incidence %>%
  filter(disease == "CWD") -> data_leaf_incidence_CWD
```

### Compute models

Select only top portion of the shrub and change leaf incidence of 1 to 0.999 to respect range of beta distribution

```{r include=FALSE}
# Models
data_leaf_incidence_CWD %>%
  filter(portion =="Top", !is.na(leaf_incidence)) %>%
  mutate(leaf_incidence = case_when(leaf_incidence == 1 ~ 0.999,
                              .default = leaf_incidence)) -> CWD_top
```


```{r}
full_model_CWD_branch_incidence <-  glmmTMB(formula = leaf_incidence ~ Shade_tree_species * distance * Coffee_Variety   + (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/sample_code),
                            ziformula = ~ 1,
                            family = beta_family(),
                            data = CWD_top,
                    na.action = "na.fail")

MuMIn::dredge(global.model = full_model_CWD_branch_incidence,
                fixed = c("cond(distance)", "cond(Shade_tree_species)",
                          "cond(distance:Shade_tree_species)")) -> dd_CWD_branch_incidence

length(dd_CWD_branch_incidence[[1]])

```

```{r}
for(i in 1:5){
  CWD_top %>%
    leaf_incidence.mod.func(frml = formula(MuMIn::get.models(dd_CWD_branch_incidence, i)[[1]]),
                            zifrml = formula("~1"),
                            disprml = formula("~1")
                            
    )
   print(formula(MuMIn::get.models(dd_CWD_branch_incidence, i)[[1]]))
  } 
```

```{r}
subset(dd_CWD_branch_incidence, delta < 4)
```

```{r}
MuMIn::get.models(dd_CWD_branch_incidence, 1)[[1]] -> selected_model_shrub_incidence_CWD
```

### Model estimation

```{r}
# Anova Model 4
car::Anova(selected_model_shrub_incidence_CWD) %>%
  round(2)
```

## 4.5 CLR leaf incidence model

```{r include=FALSE}
data_leaf_incidence %>%
  filter(disease == "CLR") %>%
  mutate(Coffee_Variety = as.factor(as.character(Coffee_Variety)))-> data_leaf_incidence_CLR
```

### Compute models

Select only lower portion of the shrub and change leaf incidence of 1 to 0.999 to respect range of beta distribution

```{r include=FALSE}
# Models
data_leaf_incidence_CLR %>%
  filter(portion == "lower", !is.na(leaf_incidence)) %>%
  mutate(leaf_incidence = case_when(leaf_incidence == 1 ~ leaf_incidence*0.999,
                              .default = leaf_incidence)) -> CLR_low
```


```{r}
full_model_CLR_branch_incidence <-  glmmTMB(formula = leaf_incidence ~ Shade_tree_species * distance * Coffee_Variety  + (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/sample_code),
                            ziformula = ~ 1,
                            family = beta_family(),
                            data = CLR_low,
                    na.action = "na.fail")

MuMIn::dredge(global.model = full_model_CLR_branch_incidence,
                fixed = c("cond(distance)", "cond(Shade_tree_species)",
                          "cond(distance:Shade_tree_species)")) -> dd_CLR_branch_incidence

length(dd_CLR_branch_incidence[[1]])

```
```{r}
subset(dd_CLR_branch_incidence, delta < 2)
```

```{r}
for(i in 1:5){
  CLR_low %>%
    leaf_incidence.mod.func(frml = formula(MuMIn::get.models(dd_CLR_branch_incidence, i)[[1]]),
                            zifrml = formula("~1"),
                            disprml = formula("~1")
                            
    )
   print(formula(MuMIn::get.models(dd_CLR_branch_incidence, i)[[1]]))
  } 
```

```{r}
full_model_CLR_branch_incidence_disp <-  glmmTMB(formula = leaf_incidence ~ Shade_tree_species * distance * Coffee_Variety + (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/sample_code),
                            ziformula = ~ 1,
                            dispformula = ~ log_total_count,
                            family = beta_family(),
                            data = CLR_low,
                    na.action = "na.fail")

MuMIn::dredge(global.model = full_model_CLR_branch_incidence_disp,
                fixed = c("cond(distance)", "cond(Shade_tree_species)",
                          "cond(distance:Shade_tree_species)")) -> dd_CLR_branch_incidence_disp

length(dd_CLR_branch_incidence_disp[[1]])

```
```{r}
subset(dd_CLR_branch_incidence_disp, delta < 2)
```

```{r}
for(i in 1:5){
  CLR_low %>%
    leaf_incidence.mod.func(frml = formula(MuMIn::get.models(dd_CLR_branch_incidence_disp, i)[[1]]),
                            zifrml = formula("~1"),
                            disprml = formula("~log_total_count")
                            
    )
   print(formula(MuMIn::get.models(dd_CLR_branch_incidence_disp, i)[[1]]))
  } 
```

```{r}
full_model_CLR_branch_incidence_disp_zi <-  glmmTMB(formula = leaf_incidence ~ Shade_tree_species * distance * Coffee_Variety  + (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/sample_code),
                            ziformula = ~ Coffee_Variety,
                            dispformula = ~ log_total_count,
                            family = beta_family(),
                            data = CLR_low,
                    na.action = "na.fail")

MuMIn::dredge(global.model = full_model_CLR_branch_incidence_disp_zi,
                fixed = c("cond(distance)", "cond(Shade_tree_species)",
                          "cond(distance:Shade_tree_species)")) -> dd_CLR_branch_incidence_disp_zi

length(dd_CLR_branch_incidence_disp_zi[[1]])

```

```{r}
subset(dd_CLR_branch_incidence_disp_zi, delta < 30)
```

```{r}
for(i in 1:5){
  CLR_low %>%
    leaf_incidence.mod.func(frml = formula(MuMIn::get.models(dd_CLR_branch_incidence_disp_zi, i)[[1]]),
                            zifrml = formula("~Coffee_Variety"),
                            disprml = formula("~log_total_count")
                            
    )
   print(formula(MuMIn::get.models(dd_CLR_branch_incidence_disp_zi, i)[[1]]))
  } 
```

```{r}
formula(MuMIn::get.models(dd_CLR_branch_incidence_disp_zi, 2)[[1]])
formula(MuMIn::get.models(dd_CLR_branch_incidence_disp_zi, 3)[[1]])
MuMIn::get.models(dd_CLR_branch_incidence_disp_zi, 3)[[1]] -> selected_model_shrub_incidence_CLR
length(dd_CLR_branch_incidence_disp_zi)
```



```{r}
# Anova
car::Anova(selected_model_shrub_incidence_CLR) %>%
  round(2) 
car::Anova(selected_model_shrub_incidence_CLR,component = "zi") %>%
  round(2) 
car::Anova(selected_model_shrub_incidence_CLR,component = "disp") %>%
  round(2)

```

### Model estimation

```{r}
marginaleffects::datagrid(model = selected_model_shrub_incidence_CLR, Coffee_Variety =c("Clone A", "Clone B", "Clone C", "Clone F", "Op1", "Op2") , grid_type = "counterfactual") -> datagrid_leaf_incidence_CLR

marginaleffects::avg_predictions(
  selected_model_shrub_incidence_CLR,
  variables = "Coffee_Variety",
  type = "response",
  newdata = datagrid_leaf_incidence_CLR
) -> CLR_leaf_incidence_variety 

marginaleffects::avg_comparisons(
  selected_model_shrub_incidence_CLR,
  variables = list(Coffee_Variety = "pairwise")
) %>%
  marginaleffects::hypotheses(multcomp = "BH") -> contrast_CLR_leaf_incidence_variety_df

get_significance_letters3(contrast_CLR_leaf_incidence_variety_df) %>%
  mutate(variable = factor(variable , levels = levels(data_leaf_incidence_CLR$Coffee_Variety))) %>%
  arrange(variable) %>%
  mutate(x= as.numeric(variable))-> compl_letter_CLR_leaf_incidence_var

CLR_leaf_incidence_variety %>%
  ggplot(aes(x = Coffee_Variety, y = estimate)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), linewidth = 1) +
  scale_y_continuous(limits = c(0,0.5))+
  geom_text(data = compl_letter_CLR_leaf_incidence_var, aes(x = x, y =0.45, label = .group), vjust = 0)+
  labs(x= "Variety", y = "CLR incidence proportion per branch")+
  theme_classic()+
  theme(aspect.ratio = 1,
        axis.text.x = element_text(colour = "black", size=13, face="italic", angle = 18, vjust =1, hjust =1),
        axis.text.y = element_text(colour = "black", size=13, face="italic"),
        axis.title = element_text(colour = "black", size=16)) -> p_CLR_leaf_incidence_variety

p_CLR_leaf_incidence_variety

```

```{r}
marginaleffects::datagrid(model = selected_model_shrub_incidence_CLR, distance =c(0, 5, 10, 15,20) , grid_type = "counterfactual") -> datagrid_leaf_incidence_CLR2

marginaleffects::avg_predictions(
  selected_model_shrub_incidence_CLR,
  variables = "distance",
  type = "response",
  newdata = datagrid_leaf_incidence_CLR2
) -> CLR_leaf_incidence_distance

CLR_leaf_incidence_distance %>%
 ggplot()+
  geom_point(data = CLR_low, aes(distance,leaf_incidence),
             alpha = 0.6, shape = 21, cex = 3, color="black",fill = "gray",show.legend = F)+
  geom_ribbon(aes(distance,estimate, ymin= conf.low, ymax = conf.high), alpha = 0.4, linewidth = 1) +
  geom_line(aes(x=distance,estimate), linewidth = 1) +
  scale_y_continuous(limits = c(0,1))+
  labs(x = "Distance from\n shade tree (m)", y = "CLR incidence proportion per branch") +
  scale_fill_viridis(option = "viridis",discrete = T )+
  scale_color_viridis(option = "viridis",discrete = T )+
  theme_classic()+
  theme(aspect.ratio = 1,
        axis.text.x = element_text(colour = "black", size=13, face="italic", angle = 18, vjust =1, hjust =1),
        axis.text.y = element_text(colour = "black", size=13, face="italic"),
        axis.title = element_text(colour = "black", size=16, face="bold"),
        panel.border = element_rect(colour = "black", fill = NA, linewidth = 1),
        legend.title = element_text(colour = "black", size=16,
                                    hjust =0.5),

        legend.text = element_text(colour = "black", size=13))   -> p_CLR_leaf_incidence_distance

p_CLR_leaf_incidence_distance

marginaleffects::avg_slopes(
  selected_model_shrub_incidence_CLR,
  variables = "distance",
  type = "response",
  new_data = datagrid_leaf_incidence_CLR2
)
```




```{r}
BES_leaf_incidence_variety %>%
  as.data.frame %>%
  mutate(disease = "BES") -> BES_sev_var_temp
# CWD_leaf_incidence_variety%>%
#   as.data.frame %>%
#   mutate(disease = "CWD") -> CWD_sev_var_temp
CLR_leaf_incidence_variety%>%
  as.data.frame %>%
  mutate(disease = "CLR") -> CLR_sev_var_temp

BES_sev_var_temp %>%
  # bind_rows(CWD_sev_var_temp) %>%
  bind_rows(CLR_sev_var_temp) %>%
  mutate(disease = factor(disease, levels = c("CLR","BES"))) %>%
  ggplot() +
  geom_violin(data = data_leaf_incidence %>%
                        dplyr::filter(organ=="leaves") %>%
                        mutate(disease = case_when(disease == "CRBD" ~ "BES",
                                .default = disease),
                                disease = factor(disease, levels = c("CLR", "CWD", "BES"))
                               ),
              aes(x = Coffee_Variety, y=leaf_incidence, fill = disease, col = disease), 
              position = position_dodge(width=0.6),scale = "width", alpha = 0.5) +
  geom_pointrange(aes(x = Coffee_Variety, y =   estimate, ymin = conf.low, ymax = conf.high, group = disease),
                   position = position_dodge(width=0.8),  cex = 0.7, linewidth = 1) +
  geom_text(data = compl_letter_CLR_leaf_incidence_var, aes(x = x-0.2, y =CLR_sev_var_temp$estimate+0.06, label = .group), vjust = 0)+
  geom_text(data = compl_letter_BES_leaf_incidence_var, aes(x = x+0.2, y =BES_sev_var_temp$estimate+0.06, label = .group), vjust = 0)+
  # geom_text(data = compl_letter_CWD_leaf_incidence_var, aes(x = x+0.2, y =CWD_sev_var_temp$estimate+0.06, label = .group), vjust = 0)+
  labs(x = "Coffee Varieties", y =  "Disease incidence proportion per branch", col = "Diseases", fill = "Diseases")+
  scale_fill_viridis(discrete = T) +
  scale_color_viridis(discrete = T) +
  theme_classic()+
  theme(aspect.ratio = 1,
        axis.text.x = element_text(colour = "black", size=13, face="italic", angle = 18, vjust =1, hjust =1),
        axis.text.y = element_text(colour = "black", size=13, face="italic"),
        axis.title = element_text(colour = "black", size=16, face="bold"),
        panel.border = element_rect(colour = "black", fill = NA, linewidth = 1),
        legend.title = element_text(colour = "black", size=16,
                                    hjust =0.5),

        legend.text = element_text(colour = "black", size=13)) -> leaf_incidence_variety

BES_sev_var_temp %>%
  # bind_rows(CWD_sev_var_temp) %>%
  bind_rows(CLR_sev_var_temp) %>%
  mutate(disease = factor(disease, levels = c("CLR","BES"))) %>% view
  
leaf_incidence_variety
```

# Figures article

```{r}
plot_cwd_shrub_incidence

p_CLR_leaf_incidence_distance# p_crl_trend
leaf_incidence_variety

ggsave(plot = plot_cwd_shrub_incidence, file="results/figures/plot_cwd_shrub_incidence.pdf",
width=25, height=15,units ="cm")

ggsave(plot = p_CLR_leaf_incidence_distance, file="results/figures/plot_clr_leaf_incidence_distance.pdf",
width=25, height=15,units ="cm")
ggsave(plot = leaf_incidence_variety, file="results/figures/leaf_incidence_variety.pdf",
width=20, height=15, units ="cm")
```

# Figures appendix

```{r}
disease_shrub_incidence
disease_correlation_plot

ggsave(plot = disease_shrub_incidence, file="results/figures/appendix/disease_shrub_incidence_shade_tree.pdf",
width=20, height=15, units ="cm")
ggsave(plot = disease_correlation_plot, file="results/figures/appendix/disease_correlation_plot.pdf",
width=20, height=15, units ="cm")
```


```{r}
pdf(file ="results/figures/appendix/res_shrub_incidence.pdf",  
    width = 10,
    height = 6) 
res_shrub_incidence <-DHARMa::simulateResiduals(selected_model_shrub_incidence, plot = T)
dev.off()

pdf(file ="results/figures/appendix/res_leaf_incidence_BES.pdf",  
    width = 10,
    height = 6) 
res_leaf_incidence_BES <- DHARMa::simulateResiduals(selected_model_shrub_incidence_BES, plot = T)
dev.off()

pdf(file ="results/figures/appendix/res_leaf_incidence_CWD.pdf",  
    width = 10,
    height = 6) 
res_leaf_incidence_CWD <- DHARMa::simulateResiduals(selected_model_shrub_incidence_CWD, plot = T)
dev.off()

pdf(file ="results/figures/appendix/res_leaf_incidence_CLR.pdf",  
    width = 10,
    height = 6) 
res_leaf_incidence_CLR <- DHARMa::simulateResiduals(selected_model_shrub_incidence_CLR, plot = T)
dev.off()

pdf(file ="results/figures/appendix/dispertion_test.pdf",  
    width = 10,
    height = 6) 
par(mfrow = c(2,2))
testDispersion(res_shrub_incidence)
title("shrub_incidence CWD")
testDispersion(res_leaf_incidence_BES)
title("leaf_incidence BES")
testDispersion(res_leaf_incidence_CWD)
title("leaf_incidence CWD")
testDispersion(res_leaf_incidence_CLR)
title("leaf_incidence CLR")

dev.off()

pdf(file ="results/figures/appendix/zero_inflation_test.pdf",  
    width = 10,
    height = 6) 
par(mfrow = c(2,2))
testZeroInflation(res_shrub_incidence)
title("shrub_incidence CWD")
testZeroInflation(res_leaf_incidence_BES)
title("leaf_incidence BES")
testZeroInflation(res_leaf_incidence_CWD)
title("leaf_incidence CWD")
testZeroInflation(res_leaf_incidence_CLR)
title("leaf_incidence CLR")

dev.off()

par(mfrow = c(1,1))

```

