---
title: "Shade tree influence on coffee disease"
author: "Mathis Gheno"
date: "2024-12-05"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup-options, include = F}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

# 1 Load Packages




```{r include=FALSE}

# Data manipulation and graphic packages
library(tidyverse)
library(readxl)
library(GGally)
library(viridis)
library(ggsci)
library(patchwork)

# Model and model values extraction packages
library(glmmTMB)
library(DHARMa)
library(car)
library(modelbased)
library(performance)

main_theme = theme_minimal()+
  theme(aspect.ratio = 1,
      axis.line = element_line(colour = "black"),
      panel.border = element_blank(),
      axis.ticks =  element_line(colour = "black"),
      axis.text.x = element_text(colour = "black", size=13, face="italic"),
      axis.text.y = element_text(colour = "black", size=13, face="italic"),
      legend.title = element_text(colour = "black", size=15, hjust =0.5),
      legend.text = element_text(colour = "black", size=13),
      axis.title= element_text(size=16,face="bold"),
      strip.text = element_text(colour = "black", size=15, face ="italic")) 

```

# 2 Arrange data to long format

## 2.1 Compute shrub inscidence of diseases (at tree level)

```{r include=FALSE}
data <- read_xlsx("data/R_PhD_Data_corrected2.xlsx")

data %>%
  rename(sample_code = "Coffee_soil _sample_CODE") %>%
  # change sample names format
  mutate(sample_code = paste(sample_code,
                             str_extract(Section_of_Kaweri, "^[a-zA-Z]{4}"), sep = "_"),
         Shade_tree_soil_sample_CODE = paste(Shade_tree_soil_sample_CODE,
                             str_extract(Section_of_Kaweri, "^[a-zA-Z]{4}"), sep = "_")) %>% 
  mutate(Shade_tree_species = case_when(Shade_tree_species == "Ficus natalensis"~ "Fn",
                                        Shade_tree_species == "Albizia coriaria" ~ "Ac",
                                        Shade_tree_species == "Artocarpus heterophyllus" ~ "Ah",
                                        Shade_tree_species == "Persea americana" ~ "Pa"))-> data


# Isolate covariate from the main dataframe
covariate_data <- data %>%
  dplyr::select(Shade_tree_species, Section_of_Kaweri, sample_code, Coffee_Variety,
         Actual_distance_from_shade_tree_m, Shade_tree_soil_sample_CODE) %>%
  mutate(Coffee_Variety = case_when(Coffee_Variety== "Unidentified" ~"Op2",
                                    Coffee_Variety== "Open pollinated" ~"Op1",
                                    .default = Coffee_Variety))

# Arrange incidence data to a long data frame format and rename variables
 
data %>% 
  # Select occurrence columns 
  dplyr::select(sample_code, starts_with("inc"), starts_with("Inc")) %>%
  pivot_longer(-sample_code, values_to = "value", names_to = "value_type") %>%
  mutate(
    # Extracting "disease" (e.g., "CWD", "CLR", "BES")
    disease = str_extract(value_type, "(?<=_)[A-Z]+"),
    
    # Extracting "portion"
    portion = str_extract(value_type, "(?<=_)lower|Top|middle"),
    
    # Extracting "branch" (e.g., "1st", "2nd", "3rd", "4th")
    branch = str_extract(value_type, "\\d+(st|nd|rd|th)"),
    
    # Extracting "value_type" (e.g., "shrub_incidence" or "shrub_incidence")
    value_type = str_extract(value_type, "^[^_]+"),
    
    # change "Incidence"  to "shrub_incidence")
    value_type = str_replace_all(value_type, "[Ii]ncidence", "shrub_incidence")
  ) %>%
  # some value are above 1,  correct that:
  mutate(value = ifelse(value>=1,1,0 )) %>%
  left_join(covariate_data, by = "sample_code") %>%
  # We have incidence at the branch level (n =12) but we need to incidence at the coffee shrub level. SO we group at sample code that contain the ID of individual coffee shrub and 
  # summarize the covariate at the same time. We do that for each 3 disease.
  group_by(sample_code, disease) %>% 
  summarise(shrub_incidence = ifelse(sum(value, na.rm = T)>=1,1,0), # 0 occurrence = 0 ; 1 to 12 occurrence = 1
            n =  n(),
            distance = unique(Actual_distance_from_shade_tree_m),
            Shade_tree_species = unique(Shade_tree_species),
            Shade_tree_soil_sample_CODE = unique(Shade_tree_soil_sample_CODE),
            Coffee_Variety = unique(Coffee_Variety)) %>%
   ungroup() %>%
   # extract the section name and mutate character column to factor
   mutate(Section_of_kawerie = str_extract(sample_code,"(?<=_).+"),
          across(where(is.character), ~as.factor(.x)))-> data_shrub_incidence
str(data_shrub_incidence)
```

## 2.2 Compute disease incidence at leaves level for each branch

```{r include=FALSE}
### Isolate total cont of leaves or berries per branch
data %>%
  dplyr::select(sample_code, starts_with("No_berries"),  starts_with("No_leaves")) %>%
  pivot_longer(-sample_code, names_to = "sample_type", values_to = "total_count") %>%
  mutate(
    # Extracting "organ" ("berries" or "leaves")
    organ = str_extract(sample_type, "(?<=_)berries|leaves"),
    
    # Extracting "portion"
    portion = str_extract(sample_type, "(?<=_)lower|Top|middle"),
    
    # Extracting "branch" (e.g., "1st", "2nd", "3rd", "4th")
    branch = str_extract(sample_type, "\\d+(st|nd|rd|th)")
   ) %>%
  dplyr::select(-sample_type) -> total_number_of_leaves_or_berries

### Isolate total count of leaves or berries infected per branchs
data %>%
  dplyr::select(sample_code, starts_with("No"),  -starts_with("No_berries"),  -starts_with("No_leaves")) %>% # extract the total number of leaves/berries and the number of leaves/berries infected
  pivot_longer(-sample_code, names_to = "sample_type", values_to = "infected_count") %>%
  mutate(
     # Extracting "disease" (e.g., "CWD", "CLR", "BES")
    disease = str_extract(sample_type, "(?<=_)[A-Z]+"),
    
    # Extracting "organ" ("berries" or "leaves")
    organ = str_extract(sample_type, "(?<=_)berries|leaves"),
    
    # Extracting "portion"
    portion = str_extract(sample_type, "(?<=_)lower|Top|middle"),
    
    # Extracting "branch" (e.g., "1st", "2nd", "3rd", "4th")
    branch = str_extract(sample_type, "\\d+(st|nd|rd|th)")
   ) -> number_of_infected_leaves_or_berries

## Merge data and compute serverity per branchs
number_of_infected_leaves_or_berries %>%
  left_join(total_number_of_leaves_or_berries, by = join_by("sample_code" == "sample_code",
                                                            "branch" == "branch",
                                                            "portion" == "portion",
                                                            "organ" == "organ")) %>%
  mutate(leaf_incidence = infected_count/total_count) %>%
  left_join(covariate_data, by = "sample_code") %>%
  mutate(Shade_tree_species = as.factor(Shade_tree_species)) %>%
  rename(distance = "Actual_distance_from_shade_tree_m") %>%
  mutate(distance_class = cut(
      distance,
      breaks = c(0, 8, 16, 24),  # Specify the breakpoints for distance class
      labels = c("[0-8]", "(8-16]", "(16-22]"),  # Labels for each range
      right = F), # Indicates whether intervals are right-closed
    total_count = case_when(total_count > 250 ~ round(total_count/10), # correct error (5 branch have more than 250 leaves -> error due to one digit added when tipping)
                            .default = total_count),
    log_total_count = log(total_count),
    across(where(is.character),~as.factor(.x))) -> data_leaf_incidence
```


```{r include=FALSE}
data_leaf_incidence %>%
  filter(disease == "CWD") %>%
  select(sample_code) %>%
  distinct(sample_code) %>%
  mutate(shade_tree = str_extract(sample_code,"(^[A-Za-z]+)(\\d+)(.{4})_(.{4})", group = 1),
         coffe_shrub = str_extract(sample_code,"(^[A-Za-z]+\\d+)(.{4})_(.{4})", group = 2),
         section = str_extract(sample_code,"(^[A-Za-z]+\\d+)(.{4})_(.{4})", group = 3)) -> temp

table(temp$section)

temp %>%
  filter(section=="Kita") %>%
  pull(shade_tree) %>%
  table()/3

temp %>%
  filter(section=="Kite") %>%
  pull(shade_tree) %>%
  table()/3

temp %>%
  filter(section=="Kyam") %>%
  pull(shade_tree) %>%
  table()/3

temp %>%
  filter(section=="Luwu") %>%
  pull(shade_tree) %>%
  table()/3

temp %>%
  filter(section=="Nonv") %>%
  pull(shade_tree) %>%
  table()/3

temp %>%
  pull(shade_tree) %>%
  table()/3
```



## 2.3 Data cleaning

### 2.3.1 Tree with no leaves (to remove)

```{r include=FALSE}

data_leaf_incidence%>%
  group_by(sample_code)%>%
  summarise(total_count = sum(total_count, na.rm = T)) %>%
  filter(total_count ==0) %>%
  pull(sample_code)-> no_leave_trees
```

before removing tree with no leaves

```{r}
data_shrub_incidence %>%
  group_by(Shade_tree_species, disease) %>%
  mutate(n_tot = n(),
            infected_count = sum(shrub_incidence,na.rm  =T)) %>%
  ggplot()+
  facet_wrap(~disease) +
  geom_bar(aes(Shade_tree_species, fill = as.factor(shrub_incidence)), position = "fill") +
  geom_text(aes(x=Shade_tree_species, y=0.2,group = Shade_tree_species, label = infected_count), col = "white") +
  geom_text(aes(x=Shade_tree_species, y=1.04,group = Shade_tree_species, label = n_tot)) +
  scale_fill_startrek() +
  labs(x = " Shade tree", y = "Proportion", fill = "Whole shrub\n incidence") +
  main_theme +
    theme(
        axis.text.x = element_text(colour = "black", size=14, face="italic", angle = 45, vjust = 1, hjust = 1))

data_shrub_incidence %>%
  group_by(Shade_tree_species, Coffee_Variety,disease) %>%
  mutate(n_tot = n(),
            infected_count = sum(shrub_incidence,na.rm  =T)) %>%
  ggplot()+
  facet_wrap(~Coffee_Variety*disease) +
  geom_bar(aes(Shade_tree_species, fill = as.factor(shrub_incidence)), position = "fill") +
  geom_text(aes(x=Shade_tree_species, y=0.2,group = Shade_tree_species, label = infected_count), col = "white") +
  geom_text(aes(x=Shade_tree_species, y=1.04,group = Shade_tree_species, label = n_tot)) +
  scale_fill_startrek() +
  labs(x = " Shade tree", y = "Proportion", fill = "Whole shrub\n incidence") +
  main_theme
```

after removing tree with no leaves
```{r}
data_shrub_incidence %>%
  filter(!(sample_code %in% no_leave_trees)) -> data_shrub_incidence

data_shrub_incidence %>%
  group_by(Shade_tree_species, disease) %>%
  mutate(n_tot = n(),
            infected_count = sum(shrub_incidence,na.rm  =T)) %>%
  ggplot()+
  facet_wrap(~disease) +
  geom_bar(aes(Shade_tree_species, fill = as.factor(shrub_incidence)), position = "fill") +
  geom_text(aes(x=Shade_tree_species, y=0.2,group = Shade_tree_species, label = infected_count), col = "white") +
  geom_text(aes(x=Shade_tree_species, y=1.04,group = Shade_tree_species, label = n_tot)) +
  scale_fill_startrek() +
  labs(x = " Shade tree", y = "Proportion", fill = "Whole shrub\n incidence") +
  main_theme +
    theme(
        axis.text.x = element_text(colour = "black", size=14, face="italic", angle = 45, vjust = 1, hjust = 1))
data_shrub_incidence %>%
  group_by(Shade_tree_species, Coffee_Variety,disease) %>%
  mutate(n_tot = n(),
            infected_count = sum(shrub_incidence,na.rm  =T)) %>%
  ggplot()+
  facet_wrap(~Coffee_Variety*disease) +
  geom_bar(aes(Shade_tree_species, fill = as.factor(shrub_incidence)), position = "fill") +
  geom_text(aes(x=Shade_tree_species, y=0.2,group = Shade_tree_species, label = infected_count), col = "white") +
  geom_text(aes(x=Shade_tree_species, y=1.04,group = Shade_tree_species, label = n_tot)) +
  scale_fill_startrek() +
  labs(x = " Shade tree", y = "Proportion", fill = "Whole shrub\n incidence") +
  main_theme
```

### 2.3.2 Under represented clones (to remove)

before removing clone H and D

```{r}
data_shrub_incidence %>%
  filter( disease == "CWD") %>%
  group_by(Shade_tree_species, Coffee_Variety) %>%
  mutate(n_tot = n(),
            infected_count = sum(shrub_incidence,na.rm  =T)) %>%
  ggplot()+
  facet_wrap(~Coffee_Variety) +
  geom_bar(aes(Shade_tree_species, fill = as.factor(shrub_incidence)), position = "fill") +
  geom_text(aes(x=Shade_tree_species, y=0.2,group = Shade_tree_species, label = infected_count), col = "white") +
  geom_text(aes(x=Shade_tree_species, y=1.04,group = Shade_tree_species, label = n_tot)) +
  scale_fill_startrek() +
  labs(x = " Shade tree", y = "Proportion", fill = "shrub_incidence") +
  main_theme
```

after removing clone H and D

```{r}
 data_shrub_incidence %>%
  filter(!(Coffee_Variety %in% c("Clone H", "Clone D"))) %>%
   mutate(Coffee_Variety  = as.factor(as.character(Coffee_Variety))) -> data_shrub_incidence
data_shrub_incidence %>%
  filter( disease == "CWD") %>%
  group_by(Shade_tree_species, Coffee_Variety) %>%
  mutate(n_tot = n(),
            infected_count = sum(shrub_incidence,na.rm  =T)) %>%
  ggplot()+
  facet_wrap(~Coffee_Variety) +
  geom_bar(aes(Shade_tree_species, fill = as.factor(shrub_incidence)), position = "fill") +
  geom_text(aes(x=Shade_tree_species, y=0.2,group = Shade_tree_species, label = infected_count), col = "white") +
  geom_text(aes(x=Shade_tree_species, y=1.04,group = Shade_tree_species, label = n_tot)) +
  scale_fill_startrek() +
  labs(x = " Shade tree", y = "Proportion", fill = "Whole shrub\n incidence") +
  main_theme
```
```{r}
 data_shrub_incidence %>%
  filter(!(Coffee_Variety %in% c("Clone H", "Clone D"))) %>%
   mutate(Coffee_Variety  = as.factor(as.character(Coffee_Variety))) -> data_shrub_incidence
data_shrub_incidence %>%
  filter( disease == "CWD") %>%
  group_by(Shade_tree_species, Coffee_Variety) %>%
  mutate(n_tot = n(),
            infected_count = sum(shrub_incidence,na.rm  =T)) %>%
  ggplot()+
  facet_wrap(~Coffee_Variety) +
  geom_bar(aes(Shade_tree_species))+
  geom_text(aes(x=Shade_tree_species, y=1.5,group = Shade_tree_species, label = n_tot)) +

  labs(x = " Shade tree", y = "n replicats of the combinaison") +
  main_theme
```

```{r}
data_shrub_incidence %>%
  filter(!(Coffee_Variety %in% c("Clone H", "Clone D"))) %>%
   mutate(Coffee_Variety  = as.factor(as.character(Coffee_Variety))) -> data_shrub_incidence
data_shrub_incidence %>%
  filter( disease == "CWD") %>%
  group_by(Section_of_kawerie, Coffee_Variety) %>%
  mutate(n_tot = n(),
            infected_count = sum(shrub_incidence,na.rm  =T)) %>%
  ggplot()+
  facet_wrap(~Coffee_Variety) +
  geom_bar(aes(Section_of_kawerie))+
  geom_text(aes(x=Section_of_kawerie, y=1.5,group = Section_of_kawerie, label = n_tot)) +

  labs(x = " Shade Section_of_kawerie", y = "n replicats of the combinaison") +
  main_theme
```


```{r include=FALSE}
data_leaf_incidence %>%
  filter(!(sample_code %in% no_leave_trees))%>%
  filter(!(Coffee_Variety %in% c("Clone H", "Clone D"))) %>%
   mutate(Coffee_Variety  = as.factor(as.character(Coffee_Variety))) -> data_leaf_incidence
```



# 3 Whole shrub incidence model

```{r}
# Create a function that take input for a glm creation. Give back the model and residuals informations.
shrub_incidence.mod.func <- function(data, 
                              frml){ # Formula for fixed effect of the models
  # Compute the model
  mod_leaf_incidence <-  glmmTMB(formula = formula(frml),
                              family = binomial(),# shrub_incidence is 1 or 0 (win or lose trial) => binomial family
                              data = data)
  # Compute residuals
  res_leaf_incidence <- DHARMa::simulateResiduals(mod_leaf_incidence, plot = TRUE)


  par(mfrow = c(2, 3))
  
  # Plot to check if dispersion term or zero inflation term is needed
  testDispersion(res_leaf_incidence)
  testZeroInflation(res_leaf_incidence)
  
  # Plot residuals against some variables of interest
  plotResiduals(res_leaf_incidence, form = data$distance )
  plotResiduals(res_leaf_incidence, form = data$Shade_tree_species)
  plotResiduals(res_leaf_incidence, form = data$Section_of_kawerie)
  plotResiduals(res_leaf_incidence, form = data$Coffee_Variety)
  par(mfrow = c(1, 1))
  
  return(mod_leaf_incidence)
}
```
## 3.1 CWD whole shrub incidence data

### Compute models

Try different model, the only constrain is that we keep "distance*Shade_tree_species + (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)" .
"distance*Shade_tree_species" : are main effect and interaction in which we are interested 
"Shade_tree_soil_sample_CODE" : random effect to correct autocorrelation at the shade tree level. 
We incremental add variables or interaction to correct residuals expectation, and limit correlation between residuals and variables of interest

```{r}
data_shrub_incidence %>%
  filter(disease == "CWD") -> binary_data_CWD

table(binary_data_CWD$Shade_tree_soil_sample_CODE) %>% length()
## Compute binomial glm  
binary_data_CWD %>%
  shrub_incidence.mod.func(frml = "shrub_incidence ~ Shade_tree_species * distance + (1|Section_of_kawerie/Shade_tree_soil_sample_CODE)") -> mod_binary_shrub_incidence_CWD1
binary_data_CWD %>%
  shrub_incidence.mod.func(frml = "shrub_incidence ~ Shade_tree_species * distance  + Coffee_Variety +
                                  (1|Section_of_kawerie/Shade_tree_soil_sample_CODE)") -> mod_binary_shrub_incidence_CWD2
binary_data_CWD %>%
  shrub_incidence.mod.func(frml = "shrub_incidence ~ Shade_tree_species * (distance + Coffee_Variety) +
                                   (1|Section_of_kawerie/Shade_tree_soil_sample_CODE)") -> mod_binary_shrub_incidence_CWD3
binary_data_CWD %>%
  shrub_incidence.mod.func(frml = "shrub_incidence ~ Shade_tree_species * (distance + Coffee_Variety )+
                                  distance:Coffee_Variety  + (1|Section_of_kawerie/Shade_tree_soil_sample_CODE)") -> mod_binary_shrub_incidence_CWD4
binary_data_CWD %>%
  shrub_incidence.mod.func(frml = "shrub_incidence ~ Shade_tree_species * distance * Coffee_Variety +
                                    + (1|Section_of_kawerie/Shade_tree_soil_sample_CODE)") -> mod_binary_shrub_incidence_CWD5
```


```{r}
AIC(mod_binary_shrub_incidence_CWD1,
    mod_binary_shrub_incidence_CWD2,
    mod_binary_shrub_incidence_CWD3,
    mod_binary_shrub_incidence_CWD4,
    mod_binary_shrub_incidence_CWD5) %>%
  arrange(AIC)
```


```{r}
## Anova 
car::Anova(mod_binary_shrub_incidence_CWD2, 2) %>%
  round(2)
car::Anova(mod_binary_shrub_incidence_CWD2, 3)

performance::r2_nakagawa(mod_binary_shrub_incidence_CWD2)
```

Tendency of Coffee variety on shrub_incidence of CWD => postHoc pairwise comparison to see if there are some difference between varieties.

### Plot results

```{r}
# Function to get significance letter from a contrast dataframe (pairwise comparison dataframe)
get_significance_letters <- function(contrast_df, alpha = 0.05, level_col1 = "Level1", level_col2 = "Level2", p_col = "p") {
  # Extract levels
  all_levels <- unique(c(as.character(contrast_df[[level_col1]]), as.character(contrast_df[[level_col2]])))

  # Initialize an empty matrix of p-values
  pmat <- matrix(NA, nrow = length(all_levels), ncol = length(all_levels),
                 dimnames = list(all_levels, all_levels))

  # Fill in the matrix with provided p-values
  for (i in seq_len(nrow(contrast_df))) {
    l1 <- as.character(contrast_df[[level_col1]][i])
    l2 <- as.character(contrast_df[[level_col2]][i])
    pval <- contrast_df[[p_col]][i]
    pmat[l1, l2] <- pval
    pmat[l2, l1] <- pval
  }
  # Generate letters using multcompView
  comp <- multcompView::multcompLetters(pmat<0.05,compare = "<")$Letters

  # Prepare output dataframe
  output <- data.frame(
    variable = factor(names(comp), levels = all_levels),
    .group = comp,
    stringsAsFactors = FALSE
  )

  return(output)
}
```

```{r}

marginaleffects::avg_predictions(
  mod_binary_shrub_incidence_CWD2,
  by = "Coffee_Variety",
  type = "response"
) -> shrub_incidence_variety 

marginaleffects::avg_comparisons(
  mod_binary_shrub_incidence_CWD2,
  variables = list(Coffee_Variety = "pairwise")
) -> contrast_shrub_incidence_variety_df

# estimate_relation(mod_leaf_incidence_BES_leaves_top6, by = c("Coffee_Variety") ) -> BES_leaf_incidence_variety
# 
# estimate_contrasts(BES_leaf_incidence_variety, contrast = c("Coffee_Variety"), p_adjust = "fdr") -> contrast_BES_leaf_incidence_variety_df
# str(contrast_BES_leaf_incidence_variety_df)
# contrast_BES_leaf_incidence_variety_df %>% str

get_significance_letters2(contrast_shrub_incidence_variety_df) %>%
  mutate(variable = factor(variable , levels = levels(data_shrub_incidence$Coffee_Variety))) %>%
  arrange(variable) %>%
  mutate(x= as.numeric(variable))-> compl_letter_shrub_incidence_var
str(shrub_incidence_variety)
shrub_incidence_variety %>%
  ggplot() +
    geom_pointrange(
    aes(x= Coffee_Variety , y = estimate , ymin = conf.low, ymax = conf.high),
    size = 0.75,linewidth = 1
  ) +
  geom_text(data = compl_letter_shrub_incidence_var, aes(x = x, y =0.95, label = .group), vjust = 0) +
  scale_y_continuous(limits = c(0,1)) +
  labs(x= "Coffee Varieties", y = "CWD shrub incidence probability") +
  theme_classic() +
  theme(aspect.ratio = 1,
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        axis.ticks =  element_line(colour = "black"),
        axis.text.x = element_text(colour = "black", size=13, face="italic", angle = 25, vjust = 1, hjust =1),
        axis.text.y = element_text(colour = "black", size=13, face="italic"),
        legend.text = element_text(colour = "black", size=18),
        axis.title= element_text(size=16,face="bold"),
        strip.text = element_text(colour = "black", size=15, face ="italic")) -> p1_shrub_incidence
p1_shrub_incidence
```


```{r}
estimate_means
modelbased::estimate_expectation(mod_binary_shrub_incidence_CWD2,by = "Coffee_Variety") -> shrub_incidence_variety

modelbased::estimate_contrasts(shrub_incidence_variety ,
                               contrast="Coffee_Variety", p_adjust = "fdr") -> contrast_shrub_incidence_variety_df

get_significance_letters(contrast_shrub_incidence_variety_df) %>%
  mutate(variable = factor(variable , levels = levels(data_shrub_incidence$Coffee_Variety))) %>%
  arrange(variable) %>%
  mutate(x= as.numeric(variable))-> compl_letter_shrub_incidence_var



shrub_incidence_variety %>%
  ggplot() +
    geom_pointrange(
    aes(x= Coffee_Variety , y = Predicted , ymin = CI_low, ymax = CI_high),
    size = 0.75,linewidth = 1
  ) +
  geom_text(data = compl_letter_shrub_incidence_var, aes(x = x, y =0.95, label = .group), vjust = 0) +
  scale_y_continuous(limits = c(0,1)) +
  labs(x= "Coffee Varieties", y = "CWD shrub incidence probability") +
  theme_classic() +
  theme(aspect.ratio = 1,
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        axis.ticks =  element_line(colour = "black"),
        axis.text.x = element_text(colour = "black", size=13, face="italic", angle = 25, vjust = 1, hjust =1),
        axis.text.y = element_text(colour = "black", size=13, face="italic"),
        legend.text = element_text(colour = "black", size=18),
        axis.title= element_text(size=16,face="bold"),
        strip.text = element_text(colour = "black", size=15, face ="italic")) -> p1_shrub_incidence
p1_shrub_incidence
```


```{r}
modelbased::estimate_means(mod_binary_shrub_incidence_CWD2, by = c("distance", "Shade_tree_species"), backend = "emmeans") %>% 
  as.data.frame() %>%
  ggplot()+
  geom_ribbon(aes(distance,Probability, ymin= CI_low, ymax = CI_high, fill = Shade_tree_species), alpha = 0.3, linewidth = 1) +
  geom_line(aes(x=distance,Probability, col = Shade_tree_species), linewidth = 1) +
  geom_point(data = binary_data_CWD, aes(distance,shrub_incidence, fill = Shade_tree_species),
             alpha = 0.8, shape = 21, cex = 3, color="black",show.legend = F)+
  facet_grid(row = vars(Shade_tree_species), switch="both")+
  scale_y_continuous(limits = c(0,1))+
  labs(x = "Distance from\n shade tree (m)", y = "CWD shrub incidence probability") +
  scale_fill_viridis(option = "viridis",discrete = T )+
  scale_color_viridis(option = "viridis",discrete = T )+
  theme_classic()+
  theme(aspect.ratio = 1,
        plot.margin = margin(0, 0, 0, 0),
        axis.title.x = element_blank(),
        legend.position = "None",
        panel.border = element_rect(colour = "black", fill = NA, linewidth = 1),
        axis.title.y = element_text(colour = "black", size=14, face="italic")) -> p2_shrub_incidence
p2_shrub_incidence

#Slope pairwise comparison shade tree
modelbased::estimate_slopes(mod_binary_shrub_incidence_CWD2, trend = "distance", by = "Shade_tree_species", backend = "emmeans")
```


```{r}
layout2 <- c(
  patchwork::area(t = 0, l = 0, b =10, r = 3.5),
  patchwork::area(t = 0, l = 2, b = 10, r = 10)
)
p2_shrub_incidence+theme(axis.title.x =  element_text(size=16,face="bold"),
         axis.title.y =  element_text(size=16,face="bold"))+
  p1_shrub_incidence+theme(axis.title.y = element_blank())+
  patchwork::plot_layout(design = layout2) &
  theme(plot.tag.position  = c(0.25, 1),
        plot.tag = element_text(size=16,face="italic"))&
  plot_annotation(tag_levels = 'A') -> plot_cwd_shrub_incidence

plot_cwd_shrub_incidence
```


## 3.2 Recap shrub incidence

```{r}
data_shrub_incidence %>%
 mutate(disease = case_when(disease == "BES" ~ "BES",
                             .default = disease)) %>%
  mutate(Shade_tree_species) %>%
  group_by(Shade_tree_species, disease) %>%
  mutate(n_tot = n(),
            infected_count = sum(shrub_incidence,na.rm  =T)) %>%
   mutate(shrub_incidence = case_when(shrub_incidence == 1 ~ "Present",
                                    shrub_incidence == 0 ~ "Absent")) %>%
  ggplot()+
  facet_wrap(~disease) +
  geom_bar(aes(Shade_tree_species, fill = as.factor(shrub_incidence)), position = "fill") +
  geom_text(aes(x=Shade_tree_species, y=0.2,group = Shade_tree_species, label = infected_count), col = "white") +
  geom_text(aes(x=Shade_tree_species, y=1.04,group = Shade_tree_species, label = n_tot)) +
  scale_fill_viridis(discrete = T) +
  labs(x = " Shade tree species", y = "Proportion of coffee shrubs", fill = "Disease incidence\n at shrubs level") +
  theme_minimal()+
  theme(aspect.ratio = 1,
      axis.line = element_line(colour = "black"),
      panel.border = element_blank(),
      axis.ticks =  element_line(colour = "black"),
      axis.text.x = element_text(colour = "black", size=13, face="italic"),
      axis.text.y = element_text(colour = "black", size=13, face="italic"),
      legend.title = element_text(colour = "black", size=15, hjust =0.5),
      legend.text = element_text(colour = "black", size=13),
      axis.title= element_text(size=16,face="bold"),
      strip.text = element_text(colour = "black", size=15, face ="italic")) -> disease_shrub_incidence

disease_shrub_incidence
```

# 4 Leaf incidence model

## 4.1 Leaf incidence correlation between diseases

```{r echo=FALSE}
data_leaf_incidence %>%
  # remove berries data (not used)
  filter(organ != "berries") %>% 
  mutate(disease = case_when(disease == "CRBD" ~ "BES", # BES on leaves = BES vs BES on berries = BES. So here we are just looking at BES becasue we only analise leaves
                           .default = disease)) %>%
  mutate(portion = case_when(portion == "lower" ~"Lower",
                             portion == "middle"~"Middle",
                             portion == "Top"~"Upper"),
         portion = factor(portion, levels = c("Upper","Middle","Lower"))) %>%
  dplyr::select(leaf_incidence, sample_code, disease,branch,portion) %>%
  pivot_wider(names_from = disease, values_from = leaf_incidence) %>% 
  dplyr::select(CWD, CLR, BES, portion) %>%
  ggpairs(columns = 1:3,
          mapping = ggplot2::aes(color = portion,
                                
                                 alpha =1),
          diag = list(continuous = wrap("barDiag", alpha=1 )),
          upper = list(continuous = wrap("cor", size = 5, alpha =1))) +
  labs(x = "Leaf incidence proportion at branch level", y = "Leaf incidence prop. (scatterplot) or branch count(barplot)")+
  # scale_color_lancet()+
  # scale_fill_lancet()+
  viridis::scale_fill_viridis( discrete = T) +
  viridis::scale_color_viridis( discrete = T) +
  theme_classic() +
  theme (axis.line = element_line(colour = "black"),
        axis.ticks =  element_line(colour = "black"),
        legend.text = element_text(colour = "black", size=18),
        axis.title= element_text(size=16,face="bold"),
        strip.text = element_text(colour = "black", size=15, face ="italic"),
        panel.border = element_rect(colour = "black", fill = NA, linewidth = 1)) -> disease_correlation_plot
disease_correlation_plot
```


### 4.2 Leaf incidence model and residual function

```{r include=FALSE}

leaf_incidence.mod.func <- function(data, 
                              frml,
                              zifrml,
                              disprml = formula("~1")){
  # Compute model
  mod_leaf_incidence <-  glmmTMB(formula = frml,
                              ziformula = zifrml,
                              dispformula = disprml,
                              family = beta_family(),
                              data = data)
  
  # Compute residuals
  res_leaf_incidence <- DHARMa::simulateResiduals(mod_leaf_incidence, plot = TRUE)


  par(mfrow = c(2, 3))
  
  # Test dispersion nand zero inflation
  testDispersion(res_leaf_incidence)
  testZeroInflation(res_leaf_incidence)
  
  # Plot residuals against some variables of interest
  plotResiduals(res_leaf_incidence, form = data$distance)
  plotResiduals(res_leaf_incidence, form = data$Shade_tree_species)
  plotResiduals(res_leaf_incidence, form = data$log_total_count)
  plotResiduals(res_leaf_incidence, form = data$Coffee_Variety)
  par(mfrow = c(1, 1))
  
  return(mod_leaf_incidence)
}

```

```{r include=FALSE}
data_leaf_incidence %>%
  ggplot() +
  facet_wrap(~disease) +
  geom_point(aes(x = log_total_count, y = leaf_incidence)) +
  labs(x = "Log(Total leaf count)", y = "Diseases leaf incidence proportion") +
  main_theme
```

## 4.3 BES Leaf incidence model

```{r include=FALSE}
data_leaf_incidence %>%
  filter(disease == "CRBD", organ =="leaves") %>%
  filter(!(Coffee_Variety %in% c("Clone H", "Clone D"))) %>%
  mutate(Coffee_Variety = as.factor(as.character(Coffee_Variety))) -> data_leaf_incidence_BES_leaves
```




### Compute models

Select only top portion of the shrub and change leaf incidence of 1 to 0.999 to respect range of beta distribution
```{r include=FALSE}
data_leaf_incidence_BES_leaves %>%
  filter(portion =="Top", !is.na(leaf_incidence)) %>%
  mutate(leaf_incidence = case_when(leaf_incidence == 1 ~ 0.999,
                                    .default = leaf_incidence)) %>%
  droplevels() -> BES_leaves_top
  # group_by(sample_code)%>%
  # summarise(infected_count = sum(infected_count),
  #           disease = unique(disease),
  #           organ = unique(organ),
  #           portion = unique(portion),
  #           total_count = sum(total_count),
  #           leaf_incidence = mean(leaf_incidence, na.rm = T),
  #           Shade_tree_species = unique(Shade_tree_species),
  #           Section_of_Kaweri = unique(Section_of_Kaweri),
  #           Coffee_Variety = unique(Coffee_Variety),
  #           distance = unique(distance),
  #           Shade_tree_soil_sample_CODE = unique(Shade_tree_soil_sample_CODE),
  #           log_total_count = log(total_count))
```

Try different model, the only constrain is that we keep "distance*Shade_tree_species + (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)" .
"distance*Shade_tree_species" : are main effect and interaction in which we are interested 
"Shade_tree_soil_sample_CODE" : random effect to correct autocorrelation between shrub at the shade tree level. 
We incremental add variables or interaction to correct residuals expectation, and limit correlation between residuals and variables of interest

```{r include=FALSE}

BES_leaves_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species *distance   + (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml = formula("~1")) -> mod_leaf_incidence_BES_leaves_top

BES_leaves_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance   + Coffee_Variety +
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml = formula("~1")) -> mod_leaf_incidence_BES_leaves_top2
BES_leaves_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance   + Coffee_Variety +
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                              zifrml = formula("~Coffee_Variety")) -> mod_leaf_incidence_BES_leaves_top3
BES_leaves_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance   + 
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                              zifrml = formula("~Coffee_Variety ")) -> mod_leaf_incidence_BES_leaves_top4
BES_leaves_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance   +
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml = formula("~Coffee_Variety"),
                    disprml = formula("~Coffee_Variety")) -> mod_leaf_incidence_BES_leaves_top5
BES_leaves_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance +
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml = formula("~Coffee_Variety"),
                    disprml = formula("~log_total_count")) -> mod_leaf_incidence_BES_leaves_top6
BES_leaves_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance +
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml = formula("~Shade_tree_species"),
                    disprml = formula("~log_total_count")) -> mod_leaf_incidence_BES_leaves_top6_test
BES_leaves_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance + Coffee_Variety +
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml = formula("~Coffee_Variety"),
                    disprml = formula("~log_total_count")) -> mod_leaf_incidence_BES_leaves_top8
BES_leaves_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance + Coffee_Variety +
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml = formula("~Coffee_Variety"),
                    disprml = formula("~Coffee_Variety")) -> mod_leaf_incidence_BES_leaves_top9
BES_leaves_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance + Coffee_Variety + Coffee_Variety:distance +
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml = formula("~Coffee_Variety"),
                    disprml = formula("~log_total_count")) -> mod_leaf_incidence_BES_leaves_top8_bis
BES_leaves_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance + Coffee_Variety + Coffee_Variety:distance +
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml = formula("~Coffee_Variety"),
                    disprml = formula("~Coffee_Variety")) -> mod_leaf_incidence_BES_leaves_top9_bis
BES_leaves_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*(distance + Coffee_Variety) +
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml = formula("~Coffee_Variety"),
                    disprml = formula("~log_total_count")) -> mod_leaf_incidence_BES_leaves_top10
BES_leaves_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*(distance + Coffee_Variety) +
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml = formula("~Coffee_Variety"),
                    disprml = formula("~Coffee_Variety")) -> mod_leaf_incidence_BES_leaves_top11
BES_leaves_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*(distance + Coffee_Variety) + distance:Coffee_Variety+
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml = formula("~Coffee_Variety"),
                    disprml = formula("~log_total_count")) -> mod_leaf_incidence_BES_leaves_top12
BES_leaves_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*(distance + Coffee_Variety) + distance:Coffee_Variety+
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml = formula("~Coffee_Variety"),
                    disprml = formula("~Coffee_Variety")) -> mod_leaf_incidence_BES_leaves_top13

# convegence issues
BES_leaves_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance * Coffee_Variety +
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml = formula("~Coffee_Variety"),
                    disprml = formula("~log_total_count")) -> mod_leaf_incidence_BES_leaves_top14

BES_leaves_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance * Coffee_Variety +
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml = formula("~Coffee_Variety"),
                    disprml = formula("~Coffee_Variety")) -> mod_leaf_incidence_BES_leaves_top15

## Some models we've tested, either bad residuals or to complex to interpret
# BES_leaves_top%>%
#   leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance+
#                                             (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
#                     zifrml = formula("~Coffee_Variety"),
#                     disprml = formula("~log_total_count*Coffee_Variety")) -> mod_leaf_incidence_BES_leaves_top10
# BES_leaves_top%>%
#   leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*(distance+Coffee_Variety)+
#                                             (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
#                     zifrml = formula("~Coffee_Variety"),
#                     disprml = formula("~log_total_count*Coffee_Variety")) -> mod_leaf_incidence_BES_leaves_top11
# BES_leaves_top%>%
#   leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*(distance+Coffee_Variety) + distance:Coffee_Variety+
#                                             (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
#                     zifrml = formula("~Coffee_Variety"),
#                     disprml = formula("~log_total_count*Coffee_Variety")) -> mod_leaf_incidence_BES_leaves_top12
# 
# BES_leaves_top%>%
#   leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance+
#                                             (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
#                     zifrml = formula("~Coffee_Variety"),
#                     disprml = formula("~log_total_count+Coffee_Variety")) -> mod_leaf_incidence_BES_leaves_top10_bis
# BES_leaves_top%>%
#   leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*(distance+Coffee_Variety)+
#                                             (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
#                     zifrml = formula("~Coffee_Variety"),
#                     disprml = formula("~log_total_count+Coffee_Variety")) -> mod_leaf_incidence_BES_leaves_top11_bis
# 
# BES_leaves_top%>%
#   leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*(distance+Coffee_Variety) + distance:Coffee_Variety+
#                                             (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
#                     zifrml = formula("~Coffee_Variety"),
#                     disprml = formula("~log_total_count+Coffee_Variety")) -> mod_leaf_incidence_BES_leaves_top12_bis


```

Coffee variety or log(total leaf) are mandatory to correct for dispersion

### Model selection

```{r}
AIC(mod_leaf_incidence_BES_leaves_top5,
    mod_leaf_incidence_BES_leaves_top6,
    #mod_leaf_incidence_BES_leaves_top7,
    mod_leaf_incidence_BES_leaves_top8,
    mod_leaf_incidence_BES_leaves_top9,
    mod_leaf_incidence_BES_leaves_top8_bis,
    mod_leaf_incidence_BES_leaves_top9_bis,
    mod_leaf_incidence_BES_leaves_top10,
    mod_leaf_incidence_BES_leaves_top11,
    mod_leaf_incidence_BES_leaves_top12,
    mod_leaf_incidence_BES_leaves_top13) %>%
  arrange(AIC)
```

### Model estimation

```{r}
# Anova
car::Anova(mod_leaf_incidence_BES_leaves_top6) %>%
  round(2)
car::Anova(mod_leaf_incidence_BES_leaves_top6, component = "zi") 

car::Anova(mod_leaf_incidence_BES_leaves_top6, component = "disp")

# performance::r2_nakagawa(mod_leaf_incidence_BES_leaves_top6,
#             null_model =   glmmTMB(formula = leaf_incidence~1,
#                               ziformula = ~1,
#                               dispformula = ~1,
#                               family = beta_family(),
#                               #weights = total_count ,
#                               data = BES_leaves_top),
#             model_component ="full")
```
```{r}
# Function to get significance letter from a contrast dataframe (pairwise comparison dataframe)
get_significance_letters2 <- function(contrast_df =contrast_BES_leaf_incidence_variety_df, alpha = 0.05, level_col1 = "Level1", level_col2 = "Level2") {
  # Extract levels
  
  split_contrast <- contrast_df$contrast %>% str_split(" - ",simplify = TRUE)
  l1 <- split_contrast[,1]
  l2 <- split_contrast[,2]
  
  all_levels <- unique(c(l1, l2))
  # Initialize an empty matrix of p-values
  pmat <- matrix(NA, nrow = length(all_levels), ncol = length(all_levels),
                 dimnames = list(all_levels, all_levels))

  # Fill in the matrix with provided p-values

  for (i in seq_len(nrow(contrast_df))) {
    pval <- contrast_df$p.value[i]
    pmat[l1[i], l2[i]] <- pval
    pmat[l2[i], l1[i]] <- pval
  }
  # Generate letters using multcompView
  comp <- multcompView::multcompLetters(pmat<0.05,compare = "<")$Letters

  # Prepare output dataframe
  output <- data.frame(
    variable = factor(names(comp), levels = all_levels),
    .group = comp,
    stringsAsFactors = FALSE
  )

  return(output)
}
```


```{r}
marginaleffects::avg_predictions(
  mod_leaf_incidence_BES_leaves_top6,
  by = "Coffee_Variety",
  type = "response"
) -> BES_leaf_incidence_variety 

marginaleffects::avg_comparisons(
  mod_leaf_incidence_BES_leaves_top6,
  variables = list(Coffee_Variety = "pairwise")
) -> contrast_BES_leaf_incidence_variety_df

# estimate_relation(mod_leaf_incidence_BES_leaves_top6, by = c("Coffee_Variety") ) -> BES_leaf_incidence_variety
# 
# estimate_contrasts(BES_leaf_incidence_variety, contrast = c("Coffee_Variety"), p_adjust = "fdr") -> contrast_BES_leaf_incidence_variety_df
# str(contrast_BES_leaf_incidence_variety_df)
# contrast_BES_leaf_incidence_variety_df %>% str

get_significance_letters2(contrast_BES_leaf_incidence_variety_df) %>%
  mutate(variable = factor(variable , levels = levels(BES_leaves_top$Coffee_Variety))) %>%
  arrange(variable) %>%
  mutate(x= as.numeric(variable))-> compl_letter_BES_leaf_incidence_var



ggplot(BES_leaf_incidence_variety, aes(x = Coffee_Variety, y = estimate)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), linewidth = 1) +
   geom_text(data = compl_letter_BES_leaf_incidence_var, aes(x = x, y =0.15, label = .group), vjust = 0)+
  labs(x= "Variety", y = "BES leaf incidence proportion")+
  theme_classic()+
  theme(aspect.ratio = 1,
        axis.text.x = element_text(colour = "black", size=13, face="italic", angle = 18, vjust =1, hjust =1),
        axis.text.y = element_text(colour = "black", size=13, face="italic"),
        axis.title = element_text(colour = "black", size=16)) -> p_BES_leaf_incidence_variety

p_BES_leaf_incidence_variety
```

## 4.4 CWD leaf incidence model

```{r include=FALSE}
data_leaf_incidence %>%
  filter(disease == "CWD") -> data_leaf_incidence_CWD
```

### Compute models

Select only top portion of the shrub and change leaf incidence of 1 to 0.999 to respect range of beta distribution

```{r include=FALSE}
# Models
data_leaf_incidence_CWD %>%
  filter(portion =="Top", !is.na(leaf_incidence)) %>%
  mutate(leaf_incidence = case_when(leaf_incidence == 1 ~ 0.999,
                              .default = leaf_incidence))-> CWD_top
```

Try different model, the only constrain is that we keep "distance*Shade_tree_species + (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)" .
"distance*Shade_tree_species" : are main effect and interaction in which we are interested 
"Shade_tree_soil_sample_CODE" : random effect to correct autocorrelation between shrub at the shade tree level. 
We incremental add variables or interaction to correct residuals expectation, and limit correlation between residuals and variables of interest

```{r include=FALSE}
CWD_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance + (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml =  formula("~1")) -> mod_leaf_incidence_CWD_top


CWD_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance   + Coffee_Variety + 
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                     zifrml =  formula("~1")) -> mod_leaf_incidence_CWD_top2
CWD_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance+(distance*Coffee_Variety) +
                                   (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml =  formula("~1")) -> mod_leaf_incidence_CWD_top2_bis
CWD_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance  + 
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                              zifrml = formula("~Coffee_Variety")) -> mod_leaf_incidence_CWD_top3
CWD_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance   + Coffee_Variety + 
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                              zifrml = formula("~Coffee_Variety")) -> mod_leaf_incidence_CWD_top4
CWD_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance  + 
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                              zifrml = formula("~Shade_tree_species")) -> mod_leaf_incidence_CWD_top5
CWD_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance  + 
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                              zifrml = formula("~Coffee_Variety")) -> mod_leaf_incidence_CWD_top6
CWD_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance + Coffee_Variety+
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                              zifrml = formula("~Coffee_Variety"),
                              disprml= formula("~log_total_count"))-> mod_leaf_incidence_CWD_top7
CWD_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance + Coffee_Variety+Coffee_Variety:distance+
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                              zifrml = formula("~Coffee_Variety"),
                              disprml= formula("~log_total_count"))-> mod_leaf_incidence_CWD_top8

### adding more to the model lead to non-convergence issues
CWD_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance*Coffee_Variety +
                                   (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml =  formula("~1")) -> mod_leaf_incidence_CWD_top9
CWD_top%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*(distance + Coffee_Variety) +
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                              zifrml = formula("~Coffee_Variety"),
                              disprml= formula("~log_total_count"))-> mod_leaf_incidence_CWD_top10
```

### Model selection

```{r}
# dplyr::select model
AIC(mod_leaf_incidence_CWD_top,
    mod_leaf_incidence_CWD_top2_bis,
    mod_leaf_incidence_CWD_top6,
    mod_leaf_incidence_CWD_top7, 
    mod_leaf_incidence_CWD_top8) %>%
  round(1) %>%
  arrange(AIC)
```
### Model estimation

```{r}
# Anova Model 4
car::Anova(mod_leaf_incidence_CWD_top8) %>%
  round(2)
car::Anova(mod_leaf_incidence_CWD_top8,component = "zi") %>%
  round(2)
car::Anova(mod_leaf_incidence_CWD_top8,component = "disp") %>%
  round(2)
```


```{r}
modelbased::estimate_slopes(mod_leaf_incidence_CWD_top8, "distance",by = "Coffee_Variety") %>% 
  as.data.frame() %>%
  ggplot() +
  geom_pointrange(aes(y = Coffee_Variety, x = Slope, xmin = CI_low, xmax = CI_high),cex = 0.7, linewidth = 1) +
  geom_vline(xintercept = 0, cex = 1, linetype = 3, color = "red") +
  #facet_grid(rows = vars(type), scales = "free_y")+
  labs(x= "Estimated distance slopes for CWD leaf incidence proportion", y = "Coffee varieties", col = "Slope type")+
  scale_color_d3()+
  theme_classic()+
  theme(aspect.ratio = 1,
        
        axis.text.x = element_text(colour = "black", size=13, face="italic", angle = 18, vjust =1, hjust =1),
        axis.text.y = element_text(colour = "black", size=13, face="italic"),
        axis.title = element_text(colour = "black", size=16),
        panel.border = element_rect(colour = "black", fill = NA, linewidth = 1),
        legend.title = element_text(colour = "black", size=16,
                                    hjust =0.5),
        legend.text = element_text(colour = "black", size=13)) -> p_CWD_trend_variety
p_CWD_trend_variety
```

```{r}
modelbased::estimate_contrasts(mod_leaf_incidence_CWD_top8,"Coffee_Variety",estimate = "typical", p_adjust = "fdr") -> contrast_CWD_leaf_incidence_variety_df

get_significance_letters(contrast_CWD_leaf_incidence_variety_df) %>%
  mutate(variable = factor(variable , levels = levels(data_leaf_incidence_CWD$Coffee_Variety))) %>%
  arrange(variable) %>%
  mutate(x= as.numeric(variable))-> compl_letter_CWD_leaf_incidence_var

modelbased::estimate_means(mod_leaf_incidence_CWD_top8,"Coffee_Variety",estimate = "typical") -> CWD_leaf_incidence_variety
ggplot(CWD_leaf_incidence_variety, aes(x = Coffee_Variety, y = Proportion)) +
  geom_pointrange(aes(ymin = CI_low, ymax = CI_high), linewidth = 1) +
   geom_text(data = compl_letter_CWD_leaf_incidence_var, aes(x = x, y =0.05, label = .group), vjust = 0)+
  labs(x= "Variety", y = "CWD leaf_incidence")+
  theme_classic()+
  theme(aspect.ratio = 1,
        axis.text.x = element_text(colour = "black", size=13, face="italic", angle = 18, vjust =1, hjust =1),
        axis.text.y = element_text(colour = "black", size=13, face="italic"),
        axis.title = element_text(colour = "black", size=16)) -> p_CWD_leaf_incidence_variety

p_CWD_leaf_incidence_variety
```

## 4.5 CLR leaf incidence model

```{r include=FALSE}
data_leaf_incidence %>%
  filter(disease == "CLR") %>%
  mutate(Coffee_Variety = as.factor(as.character(Coffee_Variety)))-> data_leaf_incidence_CLR
```

### Compute models

Select only lower portion of the shrub and change leaf incidence of 1 to 0.999 to respect range of beta distribution

```{r include=FALSE}
# Models
data_leaf_incidence_CLR %>%
  filter(portion == "lower", !is.na(leaf_incidence)) %>%
  mutate(leaf_incidence = case_when(leaf_incidence == 1 ~ leaf_incidence*0.999,
                              .default = leaf_incidence)) -> CLR_low
```

Try different model, the only constrain is that we keep "distance*Shade_tree_species + (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)" .
"distance*Shade_tree_species" : are main effect and interaction in which we are interested 
"Shade_tree_soil_sample_CODE" : random effect to correct autocorrelation between shrub at the shade tree level. 
We incremental add variables or interaction to correct residuals expectation, and limit correlation between residuals and variables of interest

```{r include=FALSE}
CLR_low %>%
 leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance + 
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                   zifrml =  formula("~1")) -> mod_leaf_incidence_CLR_low
CLR_low %>%
 leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance   + Coffee_Variety + 
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                   zifrml = formula("~1")) -> mod_leaf_incidence_CLR_low2

CLR_low %>%
 leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance    + 
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                   zifrml = formula("~Coffee_Variety")) -> mod_leaf_incidence_CLR_low3
CLR_low %>%
 leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance    + Coffee_Variety+
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                   zifrml = formula("~Coffee_Variety")) -> mod_leaf_incidence_CLR_low4
CLR_low%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance + 
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml = formula("~Shade_tree_species")) -> mod_leaf_incidence_CLR_low5
CLR_low%>%
  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance + Coffee_Variety+
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml = formula("~Shade_tree_species")) -> mod_leaf_incidence_CLR_low6

CLR_low %>%
 leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance + Coffee_Variety +
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml = formula("~Coffee_Variety"),
                    disprml =formula("~Coffee_Variety") ) -> mod_leaf_incidence_CLR_low7

CLR_low %>%
 leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance + Coffee_Variety +
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml = formula("~Coffee_Variety"),
                    disprml =formula("~log_total_count") ) -> mod_leaf_incidence_CLR_low8

CLR_low %>%
 leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance + Coffee_Variety*distance +
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml = formula("~Coffee_Variety"),
                    disprml =formula("~log_total_count") ) -> mod_leaf_incidence_CLR_low9
CLR_low %>%
 leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance + Coffee_Variety*distance + Shade_tree_species:Coffee_Variety +
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml = formula("~Coffee_Variety"),
                    disprml =formula("~log_total_count")) -> mod_leaf_incidence_CLR_low10

CLR_low %>%
 leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance *Coffee_Variety+
                                            (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
                    zifrml = formula("~Coffee_Variety"),
                    disprml =formula("~log_total_count") ) -> mod_leaf_incidence_CLR_low11

## Some models I've tested, either bad residuals or to complex to interpret
# CLR_low %>%
#  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance *Coffee_Variety+
#                                             (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
#                     zifrml = formula("~Coffee_Variety"),
#                     disprml =formula("~log_total_count+Coffee_Variety")) -> mod_leaf_incidence_CLR_low12
# CLR_low %>%
#  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance *Coffee_Variety+ Shade_tree_species:Coffee_Variety +
#                                             (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
#                     zifrml = formula("~Coffee_Variety"),
#                     disprml =formula("~log_total_count+Coffee_Variety")) -> mod_leaf_incidence_CLR_low13
# CLR_low %>%
#  leaf_incidence.mod.func(frml = formula("leaf_incidence ~  Shade_tree_species*distance + Coffee_Variety*distance +
#                                             (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
#                     zifrml = formula("~Coffee_Variety"),
#                     disprml =formula("~log_total_count*Coffee_Variety")) -> mod_leaf_incidence_CLR_low14
# CLR_low %>%
#  leaf_incidence.mod.func(frml = formula("leaf_incidence ~  Shade_tree_species*distance + Coffee_Variety*distance + Shade_tree_species:Coffee_Variety +
#                                             (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
#                     zifrml = formula("~Coffee_Variety"),
#                     disprml =formula("~log_total_count*Coffee_Variety")) -> mod_leaf_incidence_CLR_low15
# CLR_low %>%
#  leaf_incidence.mod.func(frml = formula("leaf_incidence ~ Shade_tree_species*distance *Coffee_Variety+
#                                             (1|Section_of_Kaweri/Shade_tree_soil_sample_CODE/branch)"),
#                     zifrml = formula("~Coffee_Variety"),
#                     disprml =formula("~log_total_count*Coffee_Variety")) -> mod_leaf_incidence_CLR_low16

```

### Model selection

```{r}
AIC(mod_leaf_incidence_CLR_low8,
    mod_leaf_incidence_CLR_low10,
    mod_leaf_incidence_CLR_low11) %>%
  arrange(AIC)
```

```{r}

# Anova
car::Anova(mod_leaf_incidence_CLR_low8) %>%
  round(2) 
car::Anova(mod_leaf_incidence_CLR_low8,component = "zi") %>%
  round(2) 
car::Anova(mod_leaf_incidence_CLR_low8,component = "disp") %>%
  round(2)

```

### Model estimation



```{r}
modelbased::estimate_contrasts(mod_leaf_incidence_CLR_low8,"Coffee_Variety",estimate = "typical", p_adjust = "fdr") -> contrast_CLR_leaf_incidence_variety_df

get_significance_letters(contrast_CLR_leaf_incidence_variety_df) %>%
  mutate(variable = factor(variable , levels = levels(data_leaf_incidence_CLR$Coffee_Variety))) %>%
  arrange(variable) %>%
  mutate(x= as.numeric(variable))-> compl_letter_CLR_leaf_incidence_var

modelbased::estimate_means(mod_leaf_incidence_CLR_low8,"Coffee_Variety",estimate = "typical") -> CLR_leaf_incidence_variety

CLR_leaf_incidence_variety %>%
  ggplot(aes(x = Coffee_Variety, y = Proportion)) +
  geom_pointrange(aes(ymin = CI_low, ymax = CI_high), linewidth = 1) +
  scale_y_continuous(limits = c(0,0.5))+
  geom_text(data = compl_letter_CLR_leaf_incidence_var, aes(x = x, y =0.45, label = .group), vjust = 0)+
  labs(x= "Variety", y = "CLR leaf incidence proportion")+
  theme_classic()+
  theme(aspect.ratio = 1,
        axis.text.x = element_text(colour = "black", size=13, face="italic", angle = 18, vjust =1, hjust =1),
        axis.text.y = element_text(colour = "black", size=13, face="italic"),
        axis.title = element_text(colour = "black", size=16)) -> p_CLR_leaf_incidence_variety

p_CLR_leaf_incidence_variety

```


```{r}
modelbased::estimate_contrasts(mod_leaf_incidence_CLR_low8, "Shade_tree_species", estimate = "typical", p_adjust = "fdr") -> contrast_CLR_leaf_incidence_shade_df

get_significance_letters(contrast_CLR_leaf_incidence_shade_df) %>%
  mutate(variable = factor(variable , levels = levels(data_leaf_incidence_CLR$Shade_tree_species))) %>%
  arrange(variable) %>%
  mutate(x= as.numeric(variable))-> compl_letter_CLR_leaf_incidence_shade

modelbased::estimate_means(mod_leaf_incidence_CLR_low8,"Shade_tree_species",estimate = "typical") -> CLR_leaf_incidence_shade

CLR_leaf_incidence_shade %>%
  ggplot(aes(x = Shade_tree_species, y = Proportion)) +
  geom_pointrange(aes(ymin = CI_low, ymax = CI_high), linewidth = 1) +
  scale_y_continuous(limits = c(0,0.5))+
  geom_text(data = compl_letter_CLR_leaf_incidence_shade, aes(x = x, y =0.45, label = .group), vjust = 0)+
  labs(x= "Shade tree species", y = "CLR leaf incidence proportion")+
  theme_classic()+
  theme(aspect.ratio = 1,
        axis.text.x = element_text(colour = "black", size=13, face="italic", angle = 18, vjust =1, hjust =1),
        axis.text.y = element_text(colour = "black", size=13, face="italic"),
        axis.title = element_text(colour = "black", size=16)) -> p_CLR_leaf_incidence_variety

p_CLR_leaf_incidence_variety

```



```{r}
#Slope contrast
modelbased::estimate_slopes(mod_leaf_incidence_CLR_low8,trend = "distance", by = "Shade_tree_species") %>%
  as.data.frame %>%
  rename(factors = "Shade_tree_species") %>%
  mutate(type = "Shade tree : Distance") -> clr_trend_shade

modelbased::estimate_slopes(mod_leaf_incidence_CLR_low8,trend = "distance") %>%
  as.data.frame %>%
  mutate(type = "Distance alone",
         factors ="Distance") -> clr_trend

clr_trend_shade %>%
  #bind_rows(clr_trend_var) %>%
  bind_rows(clr_trend) %>%
  mutate(factors = factor(factors, levels = c(as.character(clr_trend_shade$factors),
                                           #as.character(clr_trend_var$factors),
                                           as.character(clr_trend$factors))),
         type = factor(type, levels = c("Distance alone",
                                        "Coffee variety : Distance",
                                        "Shade tree : Distance"))) %>%
  ggplot() +
  geom_pointrange(aes(y = factors, x = Slope, xmin = CI_low, xmax = CI_high, colour = type),cex = 0.7, linewidth = 1) +
  geom_vline(xintercept = 0, linewidth = 1, linetype = 3, color = "red") +
  #facet_grid(rows = vars(type), scales = "free_y")+
  labs(x= "Estimated slopes for CLR leaf incidence proportion", y = "Slopes types", col = "Predictors")+
  scale_color_brewer(palette = "Set1")+
  theme_classic()+
  theme(aspect.ratio = 1,
       
        axis.text.x = element_text(colour = "black", size=13, face="italic", angle = 18, vjust =1, hjust =1),
        axis.text.y = element_text(colour = "black", size=13, face="italic"),
        axis.title = element_text(colour = "black", size=16, face="bold"),
        panel.border = element_rect(colour = "black", fill = NA, linewidth = 1),
        legend.title = element_text(colour = "black", size=16,
                                    hjust =0.5),
        legend.text = element_text(colour = "black", size=13)) -> p_crl_trend
p_crl_trend


```


```{r}
BES_leaf_incidence_variety %>%
  as.data.frame %>%
  mutate(disease = "BES") -> BES_sev_var_temp
CWD_leaf_incidence_variety%>%
  as.data.frame %>%
  mutate(disease = "CWD") -> CWD_sev_var_temp
CLR_leaf_incidence_variety%>%
  as.data.frame %>%
  mutate(disease = "CLR") -> CLR_sev_var_temp

BES_sev_var_temp %>%
  bind_rows(CWD_sev_var_temp) %>%
  bind_rows(CLR_sev_var_temp) %>%
  mutate(disease = factor(disease, levels = c("CLR","BES", "CWD"))) %>%
  ggplot() +
  geom_violin(data = data_leaf_incidence %>%
                        dplyr::filter(organ=="leaves") %>%
                        mutate(disease = case_when(disease == "CRBD" ~ "BES",
                                .default = disease),
                                disease = factor(disease, levels = c("CLR","BES", "CWD"))
                               ),
              aes(x = Coffee_Variety, y=leaf_incidence, fill = disease, col = disease), 
              position = position_dodge(width=0.6),scale = "width", alpha = 0.5) +
  geom_pointrange(aes(x = Coffee_Variety, y =   Proportion, ymin = CI_low, ymax = CI_high, group = disease),
                   position = position_dodge(width=0.6),  cex = 0.7, linewidth = 1) +
  geom_text(data = compl_letter_CLR_leaf_incidence_var, aes(x = x-0.2, y =CLR_sev_var_temp$Proportion+0.06, label = .group), vjust = 0)+
  geom_text(data = compl_letter_BES_leaf_incidence_var, aes(x = x, y =BES_sev_var_temp$Proportion+0.06, label = .group), vjust = 0)+
  geom_text(data = compl_letter_CWD_leaf_incidence_var, aes(x = x+0.2, y =CWD_sev_var_temp$Proportion+0.06, label = .group), vjust = 0)+
  labs(x = "Coffee Varieties", y =  "Disease leaf incidence proprotion", col = "Diseases", fill = "Diseases")+
  scale_fill_viridis(discrete = T) +
  scale_color_viridis(discrete = T) +
  theme_classic()+
  theme(aspect.ratio = 1,
        axis.text.x = element_text(colour = "black", size=13, face="italic", angle = 18, vjust =1, hjust =1),
        axis.text.y = element_text(colour = "black", size=13, face="italic"),
        axis.title = element_text(colour = "black", size=16, face="bold"),
        panel.border = element_rect(colour = "black", fill = NA, linewidth = 1),
        legend.title = element_text(colour = "black", size=16,
                                    hjust =0.5),

        legend.text = element_text(colour = "black", size=13)) -> leaf_incidence_variety


leaf_incidence_variety
```


```{r}
p_BES_leaf_incidence_variety + theme(axis.title.x = element_blank(), axis.text.x= element_blank()) +
  p_CWD_leaf_incidence_variety + theme(axis.title.x= element_blank(), axis.text.x= element_blank()) +
  p_CLR_leaf_incidence_variety +
  leaf_incidence_variety +
  plot_layout(nrow=2)

p_CWD_trend_variety

#save.image(file = "outputs/image.Rdata")
```
# Figures article

```{r}
plot_cwd_shrub_incidence 
disease_shrub_incidence
disease_correlation_plot
p_crl_trend
leaf_incidence_variety

ggsave(plot = plot_cwd_shrub_incidence, file="results/figures/plot_cwd_shrub_incidence.pdf",
width=25, height=15,units ="cm")
ggsave(plot = disease_shrub_incidence, file="results/figures/disease_shrub_incidence_shade_tree.pdf",
width=20, height=15, units ="cm")
ggsave(plot = disease_correlation_plot, file="results/figures/disease_correlation_plot.pdf",
width=20, height=15, units ="cm")
ggsave(plot = p_crl_trend, file="results/figures/p_crl_trend.pdf",
width=20, height=15, units ="cm")
ggsave(plot = leaf_incidence_variety, file="results/figures/leaf_incidence_variety.pdf",
width=20, height=15, units ="cm")
```
# Figures appendix

```{r}
pdf(file ="results/figures/appendix/res_shrub_incidence.pdf",  
    width = 10,
    height = 6) 
res_shrub_incidence <-DHARMa::simulateResiduals(mod_binary_shrub_incidence_CWD2, plot = T)
dev.off()

pdf(file ="results/figures/appendix/res_leaf_incidence_BES.pdf",  
    width = 10,
    height = 6) 
res_leaf_incidence_BES <- DHARMa::simulateResiduals(mod_leaf_incidence_BES_leaves_top6, plot = T)
dev.off()

pdf(file ="results/figures/appendix/res_leaf_incidence_CWD.pdf",  
    width = 10,
    height = 6) 
res_leaf_incidence_CWD <- DHARMa::simulateResiduals(mod_leaf_incidence_CWD_top8, plot = T)
dev.off()

pdf(file ="results/figures/appendix/res_leaf_incidence_CLR.pdf",  
    width = 10,
    height = 6) 
res_leaf_incidence_CLR <- DHARMa::simulateResiduals(mod_leaf_incidence_CLR_low8, plot = T)
dev.off()

pdf(file ="results/figures/appendix/dispertion_test.pdf",  
    width = 10,
    height = 6) 
par(mfrow = c(2,2))
testDispersion(res_shrub_incidence)
title("shrub_incidence CWD")
testDispersion(res_leaf_incidence_BES)
title("leaf_incidence BES")
testDispersion(res_leaf_incidence_CWD)
title("leaf_incidence CWD")
testDispersion(res_leaf_incidence_CLR)
title("leaf_incidence CLR")

dev.off()

pdf(file ="results/figures/appendix/zero_inflation_test.pdf",  
    width = 10,
    height = 6) 
par(mfrow = c(2,2))
testZeroInflation(res_shrub_incidence)
title("shrub_incidence CWD")
testZeroInflation(res_leaf_incidence_BES)
title("leaf_incidence BES")
testZeroInflation(res_leaf_incidence_CWD)
title("leaf_incidence CWD")
testZeroInflation(res_leaf_incidence_CLR)
title("leaf_incidence CLR")

dev.off()

par(mfrow = c(1,1))

```

